\section{\sc Publications}
                                       
                                       %\vspace*{1cm}
                                       \vspace{-0.5cm}
                                       
                                       \subsection{\small \sc Journal Publications}
                                       \vspace{-0.6cm}
                                       
                                       \small{
                                         Joint first authors are marked with * in case of equal contribution. Joint last authors are marked with $\ddag$.
                                       }
\begin{enumerate}
\item
{\bf Polishing copy number variant calls on exome sequencing data via deep learning.}
F Özden, \calkan{}$^\ddag$, AE Çiçek$^\ddag$. {\it Genome Research}, [epub June 13, 2022, doi:10.1101/gr.274845.120], 2022. \textit {Preprint: bioRxiv 2020.05.09.086082.}


\item
{\bf Fast characterization of segmental duplication structure in multiple genome assemblies.}
H Išerić, \calkan{}, F Hach, I Numanagić.
{\it Algorithms Mol Biol.}, Mar 18; 17(1):4, 2022.\\
         \hspace*{1cm}
          {\footnotesize \em presented at the 21st International Workshop on Algorithms in Bioinformatics (WABI 2021), held virtually.}


\item
{\bf Technology dictates algorithms: recent developments in read alignment.}
M Alser, J Rotman, D Deshpande, K Taraszka, H Shi, P Icer Baykal, HT Yang, V Xue, S Knyazev, BD Singer, B Balliu, D Koslicki, P Skums, A Zelikovsky, \calkan{}, O Mutlu, S Mangul.
{\it Genome Biology}, Aug 26; 22: 249, 2021.
\textit{Preprint: arXiv 2003.00110.}

\item
{\bf SneakySnake: a fast and accurate universal genome pre-alignment filter for CPUs, GPUs, and FPGAs.} M Alser, T Shahroodi, J Gomez-Luna, \calkan{}$^\ddag$, O Mutlu$^\ddag$. {\it Bioinformatics}, 36 (22-23), 5282–5290, 2020. \textit {Preprint: arXiv 1910.09020.}

 \item
 {\bf Accelerating Genome Analysis: A Primer on an Ongoing Journey.} M Alser, Z Bingöl, J Kim, D Senol Cali, S Ghose, \calkan{}, O Mutlu. {\it IEEE Micro},  40 (5): 65-75, 2020. \textit{Preprint: arXiv 2008.00961.}

 \item
 {\bf A robust benchmark for germline large deletion and insertion detection.}
 JM Zook, NF Hansen, ND Olson, LM Chapman, JC Mullikin, C Xiao, S Sherry, S Koren, AM Phillippy, PC Boutros, SME Sahraeian, V Huang, A Rouette, N Alexander, CE Mason, I Hajirasouliha, C Ricketts, J Lee, R Tearle, IT Fiddes, A Martinez-Barrio, J Wala, A Carroll, N Ghaffari, OL Rodriguez, A Bashir, S Jackman, JJ Farrell, AM Wenger, \calkan{}, A Soylev, MC Schatz, S Garg, G Church, T Marschall, K Chen, X Fan, AC English, JA Rosenfeld, W Zhou, RE Mills, JM Sage, JR Davis, MD Kaiser, JS Oliver, AP Catalano, MJP Chaisson, N Spies, FJ Sedlazeck, M Salit. 
 {\it Nature Biotechnology},  Nov;  38 (11):1347-1355, 2020.
 
\item
{\bf Apollo: A sequencing-technology-independent, scalable, and accurate assembly polishing algorithm.} C Firtina, JS Kim, M Alser, D Senol Cali, AE Cicek, \calkan{}$^\ddag$, O Mutlu$^\ddag$. {\it Bioinformatics}, 36(12): 3669-3679, 2020.
\textit{Preprint: arXiv 1902.04341.}

\item
 {\bf VALOR2: characterization of large-scale structural variants using linked-reads.}
 F Karaoglanoglu$^*$, C Ricketts$^*$, E Ebren, M Eslami Rasekh,  I Hajirasouliha$^\ddag$, \calkan{}$^\ddag$.
{\it Genome Biology}, Mar 19; 21: 72, 2020.  \textit{Preprint: bioRxiv 394528.}



   \item
         {\bf Automatic characterization of copy number polymorphism using high throughput sequencing.}  \calkan{}. {\em Turkish J Elec Eng \& Comp Sci}, 28: 253-261, 2020.
         
\item
{\bf Shouji: Fast and Efficient Computation of Banded Sequence Alignment.} M Alser, H Hassan, A Kumar, O Mutlu$^\ddag$, \calkan{}$^\ddag$.
{\em Bioinformatics}, Nov 1;   35(21): 4255–4263, 2019.


\item
 {\bf Discovery of tandem and interspersed segmental duplications using high throughput sequencing.}
 A Soylev$^*$, T Le$^*$, H Amini, \calkan{}$^\ddag$, F Hormozdiari$^\ddag$.
{\em Bioinformatics}, Oct 15;   35(20): 3923-3930, 2019.


         
\item

         {\bf Nanopore sequencing technology and tools for genome assembly: computational analysis of the current state, bottlenecks and future directions.}
         D Senol Cali, J Kim, S Ghose, \calkan{}$^\ddag$, O Mutlu$^\ddag$.
         {\em Briefings in Bioinformatics}, [epub Apr 2, 2018], Jul;   20(4): 1542–1559, 2019.

\item
         {\bf Characterizing microsatellite polymorphisms using assembly-based and mapping-based tools.}  G Demir and \calkan{}. {\em Turkish J Biol}, 432, 264-273, 2019.


         \item
         {\bf Evaluation of genome scaffolding tools using pooled clone sequencing.}  E Dal and \calkan{}. {\em Turkish J Biol}, 42, 471-476, 2018.
         
         \item

         {\bf Fast characterization of segmental duplications in genome assemblies.}
         I Numanagić,  AS Gökkaya, L Zhang, B Berger, \calkan{}$^\ddag$, F Hach$^\ddag$.
         {\em Bioinformatics}, Sep 1;   34(17): i706-714, 2018.\\
         \hspace*{1cm}
          {\footnotesize \em presented at the 17$^{th}$ European Conference for Computational Biology (ECCB 2018), September 8-12, 2018, Athens, Greece.}

                \item
                {\bf Hercules: a profile HMM-based hybrid error correction algorithm for long reads.}
                C Firtina, Z Bar-Joseph, \calkan{}$^\ddag$, AE Cicek$^\ddag$.
                {\it Nucleic Acids Research}, 46(21): e125, 2018.
                
         \item

         {\bf Realizing the potential of blockchain technologies in genomics.}
         HI Ozercan, AM Ileri, E Ayday, \calkan{}.
         {\em Genome Research}, 28(9): 1255-1263, 2018.

          \item

         {\bf GRIM-Filter: fast seed location filtering in DNA read mapping using processing-in-memory technologies.}
         J Kim, D Senol Cali, H Xin, D Lee, S Ghose, M Alser, H Hassan, O Ergin, \calkan{}$^\ddag$, O Mutlu$^\ddag$.
         {\em BMC Genomics}, 19 (Suppl 2): 89, 2018.\\
         \hspace*{1cm}
          {\footnotesize \em presented at the 16$^{th}$ Asia Pacific Bioinformatics Conference (APBC 2018), January 15-17, 2018, Yokohama, Japan.}

         \item        

         {\bf Targeting PLK1 overcomes T-DM1 resistance via CDK1-dependent phosphorylation and inactivation of Bcl-2/xL in HER2-positive breast cancer.}
         Ö. Saatci, S Borgoni, Ö. Akbulut, S Durmuş, U Raza, E Eyüpoğlu, \calkan{}, A Akyol, Ö. Kütük, S Wiemann, Ö. Şahin.         
         {\em Oncogene}, Apr;  37(17):2251-2269, 2018.

         \item        

         {\bf Computational pan-genomics: status, promises and challenges.}
         Computational Pan-Genomics Consortium. {\em Briefings in Bioinformatics}, [epub Oct 21, 2016], Jan 1; 19(1): 118-135, 2018.
         
         \item
         
         {\bf GateKeeper: a new hardware architecture for accelerating pre-alignment in DNA short read mapping.}
         M Alser, H Hassan, H Xin, O Ergin, O Mutlu$^\ddag$, \calkan{}$^\ddag$.
         {\em Bioinformatics}, Nov 1;  33(21): 3335-63, 2017.

         \item
         {\bf Toolkit for automated and rapid discovery of structural variants.}
          A Soylev, C Kockan, F Hormozdiari$^\ddag$, \calkan{}$^\ddag$.
          {\em Methods}, Oct 1; 129:3-7, 2017.
                                       
\clearpage

  \item
                                     

         {\bf Discovery and genotyping of novel sequence insertions in many sequenced individuals.}
         P Kavak, YY Lin, I Numanagić, H Asghari, T Güngör, \calkan{}$^\ddag$, F Hach$^\ddag$.
         {\em Bioinformatics} (ISMB-ECCB 2017 issue), Jul 15;  33 (14): i161-i169, 2017.\\
         \hspace*{1 cm}{\footnotesize \em presented at the 25$^{th}$ Annual International Conference on Intelligent Systems for Molecular Biology and 16$^{th}$ European Conference on 
       Computational Biology  (ISMB/ECCB 2017), 
       July 21-25, 2017, Prague, Czech Republic.}
         
  \item
                                       
         {\bf MAGNET: understanding and improving the accuracy of genome pre-alignment filtering.}
         M Alser, O Mutlu$^\ddag$, \calkan{}$^\ddag$. 
         {\em IPSI Transactions on Internet Research}, 13(2), 2017.



         
  \item        
         {\bf Building and improving reference genome assemblies.} K Meltz-Steinberg, VA Schneider, \calkan{}, MJ Montague, WC Warren, DM Church, RK Wilson.
         {\em Proceedings of the IEEE}, Mar 3, 105(3): 422-435, 2017.


  \item        
         {\bf Discovery of large genomic inversions using long
range information.} M Eslami Rasekh, G Chiatante, M Miroballo, J Tang, M Ventura, CT Amemiya, EE Eichler, F Antonacci$^\ddag$, \calkan{}$^\ddag$.
         {\em BMC Genomics}, Jan 10;  18(1): 65, 2017.

  \item        
  {\bf Inter-varietal structural variation in grapevine genomes.}
 MF Cardone, P D'Addabbo, \calkan{}, C Bergamini, CR Catacchio, F Anaclerio, G Chiatante, A Marra, G Giannuzzi, R Perniola, M Ventura, D Antonacci.
 {\em Plant Journal}, 88(4): 648-661, 2016.

  \item        
  {\bf On genomic repeats and reproducibility.}
  C Firtina and \calkan{}.
 {\em Bioinformatics}, Aug 1;   32(15): 2243-7, 2016.

  \item        
  {\bf Optimal Seed Solver: optimizing seed Selection in read mapping.}
  H Xin, S Nahar, R Zhu, J Emmons, G Pekhimenko, C Kingsford, \calkan{}$^\ddag$, O Mutlu$^\ddag$.
 {\em Bioinformatics}, Jun 1;  32(11): 1632-42, 2016.

  \item        
  {\bf Demographically-based evaluation of genomic regions under selection in domestic dogs.}
AH Freedman, RM Schweizer, D Ortega-Del Vecchyo, E Han, BW Davis, I Gronau, PM Silva, M Galaverni, Z Fan, P Marx, B Lorente-Galdos, O Ramirez, F Hormozdiari, \calkan{}, C Vilà, K Squire, 
E Geffen, J Kusak, AR Boyko, HG Parker, C Lee, V Tadigotla, A Siepel, CD Bustamante, TT Harkins, SF Nelson, T Marques-Bonet, EA Ostrander, RK Wayne, J Novembre.
 {\em PLoS Genetics}, 12(3): e1005851, 2016.

  \item        
  {\bf Determining the origin of synchronous multifocal bladder cancer by exome sequencing.} 
  Ö. Acar$^*$, E Özkurt$^*$, G Demir, H Saraç, \calkan{}, T Esen, M Somel$^\ddag$, Nathan A Lack$^\ddag$.
 {\em BMC Genomics}, Nov 9;  15: 871, 2015.

  \item        
  {\bf A global reference for human genetic variation.} The 1000 Genomes Project Consortium.  {\em Nature}, Oct 1;  526 (7571): 98-74, 2015.


  \item        
  {\bf An integrated map of structural variation in 2,504 human genomes.}
  PH Sudmant, T Rausch, EJ Gardner,  RE Handsaker, A Abyzov, J Huddleston, Y Zhang, K Ye, G Jun, MH-Y Fritz, MK Konkel, A Malhotra, AM Stütz, X Shi, FP Casale, J Chen, 
  F Hormozdiari, G Dayama, K Chen, M Malig, MJP Chaisson, K Walter, S Meiers, S Kashin, E Garrison, A Auton, HYK Lam, X J Mu, \calkan, D Antaki, T Bae, E Cerveira, P Chines, Z Chong, 
  L Clarke, E Dal, L Ding, S Emery, X Fan, M Gujral, F Kahveci, JM Kidd, Y Kong, E-W Lameijer, S McCarthy, P Flicek, RAGibbs, G Marth, CE Mason, A Menelaou, DM Muzny, 
  BJ Nelson, A Noor, NF Parrish, M Pendleton, A Quitadamo, B Raeder, EE Schadt, M Romanovitch, A Schlattl, R Sebra, AA Shabalin, A Untergasser, 
  JA Walker, M Wang, F Yu, C Zhang, J Zhang, X Zheng-Bradley, W Zhou, T Zichner, J Sebat, MA Batzer, SA McCarroll, 
  The 1000 Genomes Project Consortium, RE Mills, MB Gerstein, A Bashir, O Stegle, SE Devine, C Lee, EE Eichler, JO Korbel. 
  {\em Nature}, Oct 1;  526 (7571): 75–81, 2015.

  \item        
  {\bf Robustness of massively parallel sequencing platforms.}
  P Kavak, B Yüksel, S Aksu, MO Kulekci, T Güngör, F Hach, SC Sahinalp, Turkish Human Genome Project, {\bf {\underline {C Alkan}}}$^\ddag$,
  MS Sağıroğlu$^\ddag$.    
  {\em PLoS ONE},  Sep 18; 10(9): e0138259, 2015.  

  \item        
  {\bf Fast and accurate mapping of Complete Genomics reads.}
  D Lee, F Hormozdiari, H Xin, F Hach, O Mutlu$^\ddag$,  {\bf {\underline {C Alkan}}}$^\ddag$.
  {\em Methods}, Jun; 79-80: 3-10, 2015. 

  \item        
  {\bf Shifted Hamming Distance: a fast and accurate SIMD-friendly filter to accelerate alignment verification in read mapping.} H Xin, J Greth, J Emmons, 
G Pekhimenko, C Kingsford, {\bf {\underline{C Alkan}}}$^\ddag$,  O Mutlu$^\ddag$. {\em Bioinformatics},  May 15; 31(10): 1553-60, 2015.



  \item        
  {\bf Activating mutations of STAT5B and STAT3 in lymphomas derived from $\gamma\delta$-T or NK cells.}
   C Kucuk, B Jiang, X Hu, W Zhang, J Chan, W Xiao, N Lack,   {\bf {\underline {C Alkan}}},  J Williams, K Avery, P Kavak, A Scuto, E Sen,  P Gaulard, L Staudt, J Iqbal,  W Zhang,  A Cornish, Q Gong, Q  Yang, H Sun, F d'Amore, S Leppä, W Liu, K Fu, L de Leval, T McKeithan.
 {\em Nature Communications}, Jan 14; 6: 6025, 2015.


\clearpage
  \item        
  {\bf Whole genome sequencing of Turkish genomes reveals functional private alleles and impact of genetic interactions with Europe, Asia and Africa.}
  {\bf {\underline {C Alkan}}}, P Kavak, M Somel, O Gokcumen, S Uğurlu, E Dal, K Buğra-Bilge,  T Güngör, SC Sahinalp, N Özören, C Bekpen.
  {\em BMC Genomics}, 15 (1): 963, 2014.


  \item        
  {\bf Comparative analysis of the domestic cat genome reveals genetic signatures underlying feline biology and domestication.}
  MJ Montague, G Li, B Gandolfi, R Khan, BL Aken, SMJ Searle, P Minx, L Hillier, DC Koboldt, BW Davis, CA Driscoll, 
  CS Barr, K Blackistone, J Quilez, B Lorente-Galdos, T Marques-Bonet, {\bf {\underline {C Alkan}}}, GWC Thomas, M W Hahn, M Menotti-Raymond, 
  SJ O’Brien, R Wilson, LA Lyons, WJ Murphy, WC Warren. {\em Proc Natl Acad Sci}, Dec 2; 111(48): 17230-17235, 2014.

  \item        
  {\bf Annotated features of domestic cat – \textit{Felis catus} genome.}
  G Tamazian, S Simonov, P Dobrynin, A Makunin, A Logachev, 
  A Komissarov, A Shevchenko, V Brukhin, N Cherkasov, A Svitin,
  KP Koepfli, J Pontius, C A Driscoll, K Blackistone, C Barr, 
  D Goldman, A Antunes, J Quilez, B Lorente-Galdos,  {\bf {\underline {C Alkan}}},
  T Marques-Bonet, M Menotti-Raymond, VA David, K Narfström, SJ O’Brien.
  {\em GigaScience}, Aug 5;  3(1): 13, 2014.
       
       
       
  \item        
  {\bf mrsFAST-Ultra: a compact, SNP-aware mapper for high performance sequencing applications.}
    F Hach$^*$,
    I Sarrafi$^*$,
    F Hormozdiari,
    {\bf {\underline {C Alkan}}},
    EE Eichler,   SC Sahinalp.
    {\em Nucl Acids Research}, Jul; 42(Web Server issue): W494-500, 2014.

  \item        
         {\bf Early postzygotic mutations contribute to de novo variation in a healthy monozygotic twin pair.}
         GM Dal, B Ergüner, MS Sağıroğlu, B Yüksel, OE Onat, {\bf {\underline {C Alkan}}}, T Özçelik. 
         {\em J Med Genet}, 51(7): 455-459, 2014.

  
  \item        
         {\bf Genome sequencing highlights the dynamic early history of dogs.} 
         AH Freedman, I Gronau, RM Schweizer, D Ortega-Del Vecchyo, E Han, PM Silva, 
         M Galaverni, Z Fan, P Marx, B Lorente-Galdos, H Beale, O Ramirez, F Hormozdiari, 
         {\bf {\underline {C Alkan}}}, 
         C Vilà, K Squire, E Geffen, J Kusak, AR Boyko, HG Parker, 
         C Lee, V Tadigotla, A Siepel, CD Bustamante, TT Harkins, SF Nelson, 
         EA Ostrander, T Marques-Bonet, RK Wayne, J Novembre. 
         {\em PLoS Genetics}, 10(1): e1004016, 2014.


 \item        
        {\bf Reconstructing complex regions of genomes using long-read sequencing technology.}
         J Huddleston, S Ranade, M Malig, F Antonacci, M Chaisson, L Hon, PH Sudmant, TA Graves, 
         {\bf {\underline{C Alkan}}}, MY Dennis, RK Wilson, SW Turner, J Korlach, EE Eichler. 
         {\em Genome Research},  24(4): 688-96, 2014.


 \item        
        {\bf Rates and patterns of great ape retrotransposition.}
        F Hormozdiari, MK Konkel, J Prado-Martinez, G Chiatante, I Hernando-Herraez, JA Walker, B Nelson, {\bf {\underline {C Alkan}}}, PH Sudmant, J Huddleston, CR Catacchio, A Ko, 
        M Malig, C Baker, T Marques-Bonet, M Ventura, MA Batzer, and EE Eichler. 
        {\em Proc Natl Acad Sci}, Aug 13; 110(33): 13457-62, 2013.
                             

 \item
        {\bf Great ape genetic diversity and population history.}
        J Prado-Martinez, PH Sudmant, JM Kidd, H Li, JL Kelley, B Lorente-Galdos, KR Veeramah, AE Woerner, TD O’Connor, G Santpere, A Cagan, C Theunert, F Casals, H Laayouni, K Munch, A Hobolth, AE Halager, M Malig, J Hernandez-Rodriguez, I Hernando-Herraez, K Prüfer, M Pybus, L Johnstone, M Lachmann, {\bf {\underline {C Alkan}}}, D Twigg, N Petit, C Baker, F Hormozdiari, M Fernandez-Callejo, M Dabad, ML Wilson, L Stevison, C Camprubí, T Carvalho, A Ruiz-Herrera, L Vives, M Mele, T Abello, I Kondova, RE Bontrop, A Pusey, F Lankester, JA Kiyang, RA Bergl, E Lonsdorf, S Myers, M Ventura, P Gagneux, D Comas, H Siegismund, J Blanc, L Agueda-Calpena, M Gut, L Fulton, SA Tishkoff, JC Mullikin, RK Wilson, IG Gut, M Katherine Gonder, OA Ryder, BH Hahn, A Navarro, JM Akey, J Bertranpetit, D Reich, T Mailund, MH Schierup, C Hvilsom, AM Andrés, JD Wall, CD Bustamante, MF Hammer, EE Eichler, T Marques-Bonet. 
        {\em Nature}, 499(7459): 471-475, 2013.

        

\item
        {\bf The genome sequencing of an albino Western lowland gorilla reveals inbreeding in the wild.}
        J Prado-Martinez, I Hernando-Herraez, B Lorente-Galdos, M Dabad, O Ramirez, C Baeza-Delgado, C Morcillo-Suarez, 
        {\bf {\underline {C Alkan}}}, F Hormozdiari, E Raineri, J Estellé, M Fernandez-Callejo, M Valles, L Ritscher, T Schöneberg, E de la Calle-Mustienes, 
        S Casillas, R Rubio-Acero, M Melé, J Engelken, M Caceres, JL Gomez-Skarmeta, M Gut, J Bertranpetit, IG Gut, T Abello, 
        EE Eichler, I Mingarro, C Lalueza-Fox, A Navarro, T Marques-Bonet.
        {\em BMC Genomics}, May 31;  14(1): 363, 2013.

        
 \item
        {\bf Refinement and discovery of new hotspots of copy-number variation associated with autism spectrum disorder.}
        S Girirajan*, MY Dennis*, C Baker, M Malig, BP Coe, CD Campbell, K Mark, TH Vu,
        {\bf {\underline {C Alkan}}}, Z Cheng, LG Biesecker, R Bernier, EE Eichler.
        {\em Am J Hum Genet.}, Feb 7;  92(2): 221-37, 2013.

 \item
        {\bf Accelerating read mapping with FastHASH}
        H Xin, D Lee, F Hormozdiari, S Yedkar, O Mutlu$^\ddag$, {\bf {\underline {C Alkan}}}$^\ddag$.
        {\em BMC Genomics}, 14(Suppl 1): S13, 2013.\\
        \hspace*{1cm} {\footnotesize {\em presented at the  11$^{th}$  Asia Pacific Bioinformatics Conference,
            Jan. 21-23, 2013, Vancouver, BC, Canada}}
       
       \clearpage 
 \item
        {\bf An integrated map of genetic variation from 1,092 human genomes.}
        The 1000 Genomes Project Consortium. 
        {\em Nature}, Nov 1;  491(7422): 56-65, 2012.
        
 \item
        {\bf SCALCE: boosting sequence compression algorithms using locally consistent encoding.}
        F Hach, I Numanagi\`{c}, {\bf {\underline {C Alkan}}}, S Cenk Sahinalp.  
        {\em Bioinformatics}, Dec 1;  28(23): 3051-57, 2012.

 \item
        {\bf A high-coverage genome sequence from an archaic Denisovan individual.}
        M Meyer, M Kircher, M-T Gansauge, H Li, F Racimo, S Mallick, JG Schraiber, F Jay, K Pr\"{u}fer, C de Filippo, PH Sudmant, 
        {\bf {\underline {C Alkan}}}, Q Fu, R Do, N Rohland, A Tandon, M Siebauer, RE Green, 
        K Bryc, AW Briggs, U Stenzel, J Dabney, J Shendure, J Kitzman, MF Hammer, MV Shunkov, 
        AP Derevianko, N Patterson, AM Andr\'{e}s, EE Eichler, M Slatkin, D Reich, J Kelso, S P\"{a}\"{a}bo. 
        {\em Science}, 338(6014): 222-226, 2012.

 \item
        {\bf The bonobo genome compared with the chimpanzee and human genomes.}
        The International Gorilla Genome Sequencing and Analysis Consortium.
        {\em Nature}, 486(7404): 527-531, 2012.


\item
{\bf Insights into hominid evolution from the gorilla genome sequence.}
The International Gorilla Genome Sequencing and Analysis Consortium.
{\em Nature}, 483(7388): 169-175, 2012. 

\item
{\bf Copy number variation of individual cattle genomes using next-generation sequencing.} 
DM Bickhart. Y Hou, SG Schroeder, {\bf {\underline {C Alkan}}}, MF Cardone, LK Matukumalli, J Song, 
RD Schnabel, M Ventura, JF Taylor, JF Garcia, CP Van Tassell, TS Sonstegard, EE Eichler, GE Liu. 
{\em Genome Research}, Apr;  22(4): 778-90, 2012.

\item
MY Dennis, L Vives, K Mark, MJ Rieder, DA Nickerson, EE Eichler. {\em Nature Methods}, 9(2): 176-178, 2012.


\item
{\bf Identification and validation of a novel mature microRNA encoded by the Merkel cell polyomavirus in human Merkel cell carcinomas.}
S Lee, KG Paulson, EP Murchison, OK Afanasiev, {\bf {\underline {C Alkan}}}, JH Leonard, DR Byrd, GJ Hannon, 
P Nghiem. {\em J Clin Virol.} Nov;  52(3): 272-275, 2011. 


\item
{\bf A hexanucleotide repeat expansion in \textit{C9ORF72} is the cause of chromosome 9p21-linked ALS-FTD}  
AE Renton, E Majounie, A Waite, J Simón-Sánchez, S Rollinson, JR Gibbs, JC Schymick, H Laaksovirta, JC van Swieten, L Myllykangas, 
H Kalimo, A Paetau, Y Abramzon, AM Remes, A Kaganovich, SW Scholz, J Duckworth, J Ding, DW Harmer, DG Hernandez, JO Johnson, 
K Mok, M Ryten, D Trabzuni, RJ Guerreiro, RW Orrell, J Neal, A Murray, J Pearson, IE Jansen, D Sondervan, H Seelaar, D Blake, 
K Young, N Halliwell, JB Callister, G Toulson, A Richardson, A Gerhard, J Snowden, D Mann, D Neary, MA Nalls, T Peuralinna, 
L Jansson, VM Isoviita, AL Kaivorinne, M Hölttä-Vuori, E Ikonen, R Sulkava, M Benatar, J Wuu, A Chiò, G Restagno, 
G Borghero, M Sabatelli, The ITALSGEN Consortium, D Heckerman, E Rogaeva, L Zinman, JD Rothstein, M Sendtner, C Drepper, EE Eichler, 
{\bf {\underline {C Alkan}}}, Z Abdullaev, SD Pack, A Dutra, E Pak, J Hardy, A Singleton, NM Williams, P Heutink, S Pickering-Brown, 
HR Morris, PJ Tienari, BJ Traynor. {\em Neuron}, Oct 20;  72(2): 257-268, 2011.

\item
{\bf Gorilla genome structural variation reveals evolutionary parallelisms with chimpanzee.}
M Ventura, CR Catacchio, {\bf {\underline {C Alkan}}}, T Marques-Bonet, S Sajjadian, TA Graves, F Hormozdiari, A Navarro, 
M Malig, C Baker, C Lee, EH Turner, L Chen, JM Kidd, N Archidiacono, J Shendure, RK Wilson, EE Eichler.
{\em Genome Research}, Oct;  21(10): 1640-9, 2011.


\item
{\bf Sensitive and fast mapping of di-base encoded reads.}
F Hormozdiari*, F Hach*, SC Sahinalp, EE Eichler, {\bf {\underline {C Alkan}}}.
{\em Bioinformatics}, Jul 15;  27(14):1 915-21, 2011.



\item
{\bf \textit {Alu} repeat discovery and characterization within human genomes}.
F Hormozdiari*, {\bf {\underline {C Alkan*}}}, M Ventura*, I Hajirasouliha, M Malig, 
F Hach, D Yorukoglu, P Dao, M Bakshi, SC Sahinalp, EE Eichler.
{\em Genome Research}, Jun;  21(6): 840-9, 2011.

\item
{\bf Genome structural variation discovery and genotyping}. 
{\bf {\underline {C Alkan}}}, BP Coe, EE Eichler.
{\em Nature Reviews Genetics}, 12: 363-376, 2011.


\item
{\bf {\em Clcn4-2} genomic structure differs between the X locus in Mus spretus and the autosomal 
locus in Mus musculus: AT motif enrichment on the X}.  
DK Nguyen, F Yang, R Kaul, {\bf {\underline {C Alkan}}}, A Antonellis, KF Friery, 
B Zhu, PJ de Jong, CM Disteche. 
{\em Genome Research}, 21(3): 402-409, 2011.


\item
{\bf Mapping copy number variation at fine scale by population scale genome sequencing}.
RE Mills*, K Walter*, C Stewart*, RE Handsaker*, K Chen*, 
{\bf {\underline {C Alkan}*}}, A Abyzov*, SC Yoon*, K Ye*, RK Cheetham, 
A Chinwalla, DF Conrad, Y Fu, F Grubert, I Hajirasouliha, 
F Hormozdiari, LM Iakoucheva, Z Iqbal, S Kang, JM Kidd, 
MK Konkel, J Korn, E Khurana, D Kural, HYK Lam, J Leng, 
R Li, Y Li, C-Y Lin, R Luo, XJ Mu, J Nemesh,
HE Peckham, T Rausch, A Scally, X Shi, MP Stromberg, 
AM St\"{u}tz, A E Urban, JA Walker, J Wu, Y Zhang, 
ZD Zhang, MA Batzer, L Ding, GT Marth, G McVean, 
J Sebat, M Snyder, J Wang, K Ye, EE Eichler, 
MB Gerstein, ME Hurles, C Lee, SA McCarroll,  JO Korbel.
{\em Nature}, 470(7332): 56-65, 2011.

\clearpage
\item
{\bf Comparative and demographic analysis of orangutan genomes}. 
International Orangutan Genome Sequencing and Analysis Consortium.
{\em Nature}, 469(7331): 529-533, 2011.

\item
{\bf Haplotype resolved genome sequencing of a Gujarati Indian individual}.
JO Kitzman, AP MacKenzie, A Adey, JB Hiatt, RP Patwardhan, 
PH Sudmant, SB Ng, {\bf {\underline{C Alkan}}}, R Qiu, EE
Eichler, J Shendure.
{\em Nature Biotechnology}, 29(1): 59-63, 2011.

\item
{\bf Limitations of next-generation genome assembly}.
{\bf {\underline {C Alkan}}}, S Sajjadian, EE Eichler.
{\em Nature Methods}, 8(1):61-65, 2011. \\
\hspace*{1 cm}{\footnotesize {\it Highlighted in ``Assemblies: the good, the bad, the ugly'', E Birney, 
{\em Nature Methods}, 8(1): 59-60, 2011.}}



\item
{\bf Genome-wide characterization of centromeric satellites from multiple mammalian genomes}.
{\bf {\underline {C Alkan*}}}, MF Cardone*, CR Catacchio, F Antonacci,
 SJ O'Brien, OA Ryder, S Purgato, M Zoli, G Della Valle, EE Eichler, M Ventura.
{\em Genome Research}, 21(1): 137-145, 2011.


\item
{\bf Genetic history of an archaic hominin group from Denisova Cave in Siberia}.
D Reich, RE Green, M Kircher, J Krause, 
N Patterson, EY Durand, B Viola, AW Briggs, 
U Stenzel, PLF Johnson, T Maricic, JM Good, 
T Marques-Bonet, {\bf {\underline {C Alkan}}}, Q Fu, S Mallick, H Li, 
M Meyer, EE Eichler, M Stoneking, M Richards, 
S Talamo, MV Shunkov, AP Derevianko, J-J Hublin, 
J Kelso, M Slatkin, S P\"{a}\"{a}bo.
{\em Nature}, Dec;  468(7327): 1053-1060, 2010.

\item
{\bf Diversity of human copy number variation and multicopy genes}. PH Sudmant, JO Kitzman, F Antonacci, 
{\bf {\underline {C Alkan}}}, M Malig, A Tsalenko, N Sampas, L Bruhn, J Shendure, The 1000 Genomes Project Consortium, EE Eichler.
{\em Science}, Oct;  330(6004): 641-646, 2010.

\item
{\bf A map of human genome variation from population scale sequencing}. The 1000 Genomes Project Consortium.
{\em Nature}, Oct;  467(7319): 1061-1073, 2010.

\item
{\bf A large and complex structural polymorphism at 16p12.1 underlies microdeletion disease risk}. F Antonacci, JM Kidd,
 T Marques-Bonet, B Teague, M Ventura, S Girirajan, {\bf {\underline {C Alkan}}}, CD Campbell, L Vives, M Malig, 
JA Rosenfeld, BC Ballif, LG Shaffer, TA Graves, RK Wilson, DC Schwartz, EE Eichler. {\em Nature 
Genetics}, Sep;  42(9): 745-750, 2010.

\item
{\bf mrsFAST: a cache-oblivious algorithm for short-read mapping}. F  Hach,  F Hormozdiari, {\bf {\underline {C Alkan}}}, F Hormozdiari,
 I Birol,  EE Eichler, SC Sahinalp. {\em Nature Methods}, Aug;  7(8): 576-7, 2010.

\item
 {\bf A draft sequence of the Neandertal genome}. RE Green, J Krause, 
AW Briggs, T Maricic, U Stenzel, M Kircher, N Patterson, 
H Li, W Zhai, MH-Y Fritz, NF Hansen, EY Durand, 
A-S Malaspinas, JD Jensen, T Marques-Bonet, {\bf {\underline {C Alkan}}}, K Pr\"{u}fer, M Meyer, HA Burbano, JM Good, R Schultz, A Aximu-Petri, 
A Butthof, B H\"{o}ber, B H\"{o}ffner, M Siegemund, A Weihmann, C
Nusbaum, ES Lander, C Russ, N Novod, J Affourtit, M Egholm, 
C Verna, P Rudan, D Brajkovic, Z Kucan, I Gusic, VB 
Doronichev, LV Golovanova, C Lalueza-Fox, M de la Rasilla, J Fortea, 
A Rosas, RW Schmitz, PLF Johnson, EE Eichler, D Falush, E 
Birney, JC Mullikin, M Slatkin, R Nielsen, J Kelso, M Lachmann, 
D Reich, S P\"{a}\"{a}bo. {\em Science}, 7 May, 328(5979): 710-722, 2010. \\
\hspace*{1 cm}{\footnotesize {\it Recipient of the 2010 AAAS Newcomb Cleveland Prize.}}


\item
{\bf Characterization of missing human genome sequences and
copy-number polymorphic insertions}.
JM Kidd, N Sampas, F Antonacci, T Graves, R Fulton, HS Hayden, {\bf {\underline{C Alkan}}},
 M Malig, M Ventura, G Giannuzzi, J Kallicki, P Anderson, A Tsalenko, 
NA Yamada, P Tsang, R Kaul, RK Wilson, L Bruhn, EE Eichler.
{\em Nature Methods}, May, 7 (5):365-371, 2010.


\item
{\bf Next-generation VariationHunter: combinatorial algorithms for transposon insertion discovery}.
F Hormozdiari, I Hajirasouliha, P Dao, F Hach, D Yorukoglu, {\bf {\underline{C Alkan}}},
 EE Eichler, SC Sahinalp.
{\em Bioinformatics}, Jun 15;  26(12): i350-i357, 2010. \\
\hspace*{1cm} {\footnotesize {\em presented at the 18$^{th}$ Annual International Conference on Intelligent Systems
for Molecular Biology (ISMB 2010), July 11-13, 2010, Boston, MA, USA}}



\item
{\bf Detection and characterization of novel sequence insertions using paired-end next-generation sequencing}.
 I Hajirasouliha*, F Hormozdiari*, {\bf {\underline{C Alkan}}}*, JM Kidd, I Birol, EE Eichler,
 SC Sahinalp.
{\em Bioinformatics}, May 15; 26(10):1277-83, 2010. \\
\hspace*{1cm} {\footnotesize {\em presented at the Conference on High Throughput Sequencing Analysis and Algorithms (HiTSeq 2010), 
    Special Interest Group of ISMB 2010: July 9-10 2010, Boston, MA, USA}}

\clearpage

\item
{\bf Complete Khoisan and Bantu genomes from southern Africa}.
 SC Schuster, W Miller, A Ratan, LP Tomsho, B Giardine, LR Kasson, RS
 Harris, DC Petersen, F Zhao, J Qi, {\bf \underline{C Alkan}}, JM Kidd, Y Sun, DI Drautz, 
P Bouffard, DM Muzny, JG Reid, LV Nazareth, Q Wang, R Burhans, C Riemer, 
NE Wittekindt, P Moorjani, EA Tindall, CG Danko, WS Teo, AM Buboltz, 
Z Zhang, Q Ma, A Oosthuysen, AW Steenkamp, H Oostuisen, P Venter, J 
Gajewski, Y Zhang, BF Pugh, KD Makova, A Nekrutenko, ER Mardis, N Patterson, 
TH Pringle, F Chiaromonte, JC Mullikin, EE Eichler, RC Hardison, RA Gibbs, TT 
Harkins, VM Hayes. 
{\em Nature}, Feb, 463(7283): 943-947, 2010.

\item
{\bf Personalized copy-number and segmental duplication maps using next-generation sequencing}.
{\bf {\underline{C Alkan}}}, JM Kidd, T Marques-Bonet, G Aksay, F Antonacci, F Hormozdiari, J O Kitzman, 
C Baker, M Malig, O Mutlu, SC Sahinalp, R A Gibbs, EE Eichler.  
{\em Nature Genetics},  Oct, 41(10): 1061-1067, 2009.\\
\hspace*{1 cm}{\footnotesize {\it Highlighted in "Mapping duplicated sequences", DY Chiang and SA McCarroll, Nature Biotechnology, Nov;  27(11): 1001-2, 2009.}}


\item
{\bf Sequence and structural variation in a human genome uncovered by short-read, massively parallel ligation sequencing using two base encoding}.
KJ McKernan, HE Peckham, GL Costa, SF McLaughlin, Y Fu, EF Tsung, CR Clouser, C Duncan, JK Ichikawa, CC Lee, Z Zhang, 
SS Ranade, ET Dimalanta,  FC Hyland, TD Sokolsky, L Zhang, JA Sheridan, H Fu, CL Hendrickson, B Li, L Kotler, JR Stuart, 
JA Malek, JM Manning, AA Antipova, DS Perez, MP Moore, KC Hayashibara, MR Lyons, RE Beaudoin, BE Coleman, MW Laptewicz, 
AE Sannicandro, MD Rhodes, RK Gottimukkala, S Yang, V Bafna, A Bashir, A MacBride, {\bf \underline{C Alkan}}, JM Kidd, EE Eichler, 
MG Reese, FM De La Vega, AP Blanchard. 
{\em Genome Research}, Sep, 19(9): 1527-1541, 2009.


\item
{\bf  New insights into centromere organization and evolution from the white-cheeked gibbon and marmoset}.
A Cellamare,    CR Catacchio,  {\bf \underline{C Alkan}}, G Giannuzzi, F Antonacci, MF Cardone, G Della Valle, M Malig, M Rocchi, EE Eichler, M Ventura.
{\em Mol Biol Evol}, Aug;  26(8): 1889-1900, 2009.

\item
{\bf MoDIL: detecting small indels from clone-end sequencing with mixtures of distributions}.
S Lee, F Hormozdiari, {\bf {\underline{C Alkan}}}, M Brudno.
{\em Nature Methods},  Jul, 6(7): 473-4, 2009.

\item
{\bf  Combinatorial algorithms for structural variation detection in high throughput sequenced genomes}.
F Hormozdiari*, {\bf {\underline{C Alkan}}}*, EE Eichler, SC \c{S}ahinalp. 
{\em Genome Research}, Jul, 19(7): 1270-8, 2009.\\
\hspace*{1cm} {\footnotesize {\it presented at the
 Thirteenth Annual International Conference on Research in Computational Molecular 
Biology (RECOMB 2009), May 18-21, 2009 Tucson, AZ, USA}}



\item

{\bf Comparative analysis of Alu repeats in primate genomes}.  GE Liu, {\bf {\underline{C Alkan}}}, L Jiang, S Zhao, EE Eichler. 
{\em Genome Research}, 19(5): 876-885, 2009.




\item
{\bf Death and resurrection of the human {\em IRGM} gene}. C Bekpen, T Marques-Bonet,
{\bf {\underline{C Alkan}}}, F Antonacci, M B Leogrande, M Ventura, JM Kidd, P Siswara, J C Howard, EE Eichler. {\em PLoS Genetics}, Mar;  5(3): e1000403, 2009.

\item

{\bf A burst of segmental duplications in the genome of the African great ape ancestor}. T Marques-Bonet, JM Kidd, M Ventura, TA Graves, Z Cheng, LW Hillier, Z Jiang, 
C Baker, R Malfavon-Borja, LA Fulton, {\bf {\underline{C Alkan}}}, G Aksay, S Girirajan,
 P Siswara, L Chen, MF Cardone, A Navarro, ER Mardis,
 RK Wilson, EE Eichler. {\em Nature}, Feb 12;  457(7231): 877-881, 2009.


\item
 {\bf Mapping and sequencing of structural variation from eight human genomes}.
 JM Kidd, GM Cooper, WF Donahue, HS Hayden, 
 N Sampas, T Graves, N Hansen, B Teague, {\bf {\underline{C Alkan}}},  F Antonacci, 
 E Haugen, T Zerr, NA Yamada, P Tsang,  TL Newman, E T\"{u}z\"{u}n, 
 Z Cheng, HM Ebling, N Tusneem, R David, W Gillett, KA Phelps, 
 D Saranga, A Brand, W Tao, E Gustafson, K McKernan, L Chen, 
 M Malig, JD Smith, SA McCarroll, DA Altshuler,  
 DA Peiffer, M Dorschner, J Stamatoyannopoulos, D Schwartz,  
 DA Nickerson, JC Mullikin, RK Wilson, L Bruhn, 
 MV Olson, R Kaul, DR Smith, EE Eichler.
 {\em Nature}, May 1, 2008;  453(7191): 56-64, 2008.


\item
 {\bf Optimal design of oligonucleotide microarrays for measurement of DNA copy number}.
 AJ Sharp, A Itsara, Z Cheng, {\bf {\underline{C Alkan}}}, S Schwartz, EE Eichler.
 {\em Human Molecular Genetics}, Nov 15;  16(22): 2770-2779, 2007.


%\clearpage

\item
 {\bf Organization and evolution of primate centromeric DNA from whole genome shotgun sequence data}.
 {\bf {\underline{C Alkan}}}, M Ventura, N Archidiacono, M Rocchi, SC \c{S}ahinalp, EE Eichler.
 {\em PLoS Computational Biology}, Sep;  3(9): e181, 2007.


\item
 {\bf taveRNA: a web suite for RNA algorithms and applications}.
  C Aksay, R Salari, E Karako\c{c}, {\bf {\underline{C Alkan}}}, SC \c{S}ahinalp.
  {\em Nucleic Acids Research}, Jul 1;  35 (Web Server Issue): W325-329, 2007.

\clearpage
\item
 {\bf RNA-RNA interaction prediction and antisense RNA target search}.
  {\bf {\underline{C Alkan}}}, E Karako\c{c}, J Nadeau, SC \c{S}ahinalp,
  K Zhang.
  {\em Journal of Computational Biology}, March 2006;  Vol 13, No 2: 267-282, 2006. \\
\hspace*{1cm} {\footnotesize {\it presented at the Ninth Annual International Conference on Research in Computational Molecular Biology
    (RECOMB 2005 - LNBI 3500), pp 152-171, 
    May 14-18, 2005 Cambridge, MA, USA, 2005.}}


\item
{\bf Manipulating multiple sequence alignments via MaM and  WebMaM}.
{\bf {\underline{C Alkan}}}, E T\"{u}z\"{u}n, J Buard, F Lethiec,
EE Eichler, JA Bailey, SC \c{S}ahinalp.
{\em Nucleic Acids Research}, Jul 1;  33 (Web Server issue):
W295-W298, 2005.

\item
 {\bf The role of unequal crossover in alpha-satellite 
   DNA evolution: a computational analysis}.
  {\bf {\underline{C Alkan}}}, EE Eichler, JA Bailey, SC \c{S}ahinalp, E T\"{u}z\"{u}n.
  {\em Journal of Computational Biology}, 11(5): 933-944, 2004. \\
\hspace*{1cm}  {\footnotesize {\it presented at the 13$^{th}$ International Conference on Genome Informatics, 
December 16-18, 2002, Tokyo, Japan, 18: 93-102, 2002.}}

\item
  {\bf The structure and evolution of centromeric transition regions within
    the human genome}.
  X She, JE Horvath, Z Jiang, G Liu, T S Furey,
  L Christ, R Clark, T Graves, CL Gulden, {\bf \underline{C Alkan}}, JA Bailey, SC \c{S}ahinalp, 
  M Rocchi, D Haussler, RK Wilson, W Miller, S Schwartz, EE Eichler.
  {\em Nature}, Aug 19, 2004;  430(7002): 857-64, 2004.


\item
  {\bf Analysis of primate genomic variation reveals a repeat-driven 
    expansion of the human genome}.
  G Liu, NISC Comparative Sequencing Program, S Zhao, JA Bailey, 
  SC \c{S}ahinalp, {\bf \underline{C Alkan}}, E T\"{u}z\"{u}n, ED Green, EE Eichler.
  {\em Genome Research}, 13(3): 358-368, 2003.

\item
  {\bf Divergent origins and concerted expansion of two segmental
    duplications on 
    chromosome 16}.
  EE Eichler, ME Johnson, {\bf \underline{C Alkan}}, E T\"{u}z\"{u}n, C \c{S}ahinalp,
    D Misceo, 
    N Archidiacono, and M Rocchi.
    {\em Journal of Heredity}, 92: 462-468, 2001.

\end{enumerate}


\vspace{-.4cm}
\subsection{\small \sc  Book Chapters}
\begin{enumerate}
    \item 
       {\bf Whole-genome shotgun sequence CNV detection using read depth.}
       F Kahveci, \calkan{}.
       In: Bickhart D (eds) {\em Copy Number Variants. Methods in Molecular Biology}, vol 1833. Humana Press, New York, NY, 2018.
\end{enumerate}

\vspace{-.4cm}
\subsection{\small \sc  Peer-Reviewed Conference Proceedings}
\vspace{-.4cm}
       {\small
         %Note: In CS disciplines papers in highly ranked conferences are fully refereed 
%and are regarded as highly as the top journal papers. 
%In computational molecular biology RECOMB and ISMB are generally accepted as the 
%top conferences, with 10-15\% acceptance rates.
Note that selected papers accepted to some conferences such as ISMB and RECOMB are published
in special issues of journals. Such publications are listed under Journal Publications with a note to the conference above.
Joint first authors are marked with * in case of equal contribution.
Joint last authors are marked with $\ddag$.
}


%  \item        
%         {\bf Genome Read In-Memory (GRIM) Filter: fast seed location filtering in DNA read mapping using processing-in-memory technologies.}
%         J Kim, D S Cali, H Xin, D Lee, S Ghose, M Alser, H Hassan, O Ergin, \calkan{}$^\ddag$, O Mutlu$^\ddag$.
%         The 16$^{th}$ Asia Pacific Bioinformatics Conference (APBC 2018), January 15-17, 2018, Yokohama, Japan.


% \clearpage
%  \vspace{-.2cm}        
%         {\bf Discovery and genotyping of novel sequence insertions in many sequenced individuals.}
%         Pınar Kavak, Yen-Yi Lin, Ibrahim Numanagić, Hossein Asghari, Tunga Güngör, \calkan{}$^\ddag$, Faraz Hach$^\ddag$.
%       25$^{th}$ Annual International Conference on Intelligent Systems for Molecular Biology and 16$^{th}$ European Conference on 
%       Computational Biology  (ISMB/ECCB 2017), 
%       July 21-25, 2017, Prague, Czech Republic.

\begin{enumerate}
\item
{\bf GenASM: a low-power, memory-efficient approximate string matching acceleration framework for genome sequence analysis.}
D Senol Cali, GS Kalsi, Z Bingöl, L Subramanian, C Firtina, J Kim, R Ausavarungnirun, M Alser,
A Nori, J Gómez Luna, A Boroumand, A Scibisz, S Subramoney, \calkan{}, S Ghose, O Mutlu.
{\em 53$^{rd}$ IEEE/ACM International Symposium on Microarchitecture (MICRO 2020)}, October 17-21, 2020, Athens, Greece.

    \item 

{\bf Can you really anonymize the donors of genomic data in today's digital world?}
M Alser, N Almadhoun, A Nouri, {\bf {\underline{C Alkan}}}$^\ddag$, and E Ayday$^\ddag$. 
{\em 10$^{th}$ International Workshop on Data Privacy Management (DPM 2015)}, 
 September 21-22, 2015, Vienna, Austria.


\item

{\bf Improving genome assemblies using multi-platform sequence data.}
P Kavak, B Ergüner, D Üstek, B Yüksel, MŞ. Sağıroğlu, T Güngör and \calkan{}.
{\em 12$^{th}$ Computational Intelligence methods for Bioinformatics and Biostatistics (CIBB 2015)}, 
 September 10-12, 2015, Naples, Italy.


%\vspace{-.2cm}
%{\bf Accelerating read mapping with FastHASH}
%H Xin, D Lee, F Hormozdiari, S Yedkar, O Mutlu$^\ddag$, {\bf {\underline {C Alkan}}}$^\ddag$.
%{\em  Proc. of the 11$^{th}$  Asia Pacific Bioinformatics Conference},
%Jan. 21-23, 2013, Vancouver, BC, Canada

%\vspace{-.2cm}
%{\bf Detection and characterization of novel sequence insertions using paired-end next-generation sequencing},
% I Hajirasouliha*, F Hormozdiari*, {\bf {\underline{C Alkan}}}*, JM Kidd, I Birol, EE Eichler,
% SC Sahinalp.
%{\em  Proc. of the 11$^{th}$  Conference on High Throughput Sequencing Analysis and Algorithms, Special Interest
%Group of ISMB 2010 (HiTSeq 2010): July 9-10 2010, Boston, MA, USA}

%\vspace{-.2cm}
%{\bf Next-generation VariationHunter: combinatorial algorithms for transposon insertion discovery}.
%F Hormozdiari, I Hajirasouliha, P Dao, F Hach, D Yorukoglu, {\bf {\underline{C Alkan}}},
% EE Eichler, SC Sahinalp.
%{\em Proc. of the 18$^{th}$ Annual International Conference on Intelligent Systems
%for Molecular Biology (ISMB 2010)}, July 11-13, 2010, Boston, MA, USA


%\clearpage

%\vspace{-.2cm}
%{\bf  Combinatorial algorithms for structural variation detection in high throughput sequenced genomes}.
%F Hormozdiari*, {\bf {\underline{C Alkan}}}*, EE Eichler, SC \c{S}ahinalp.
%{\em Proc. of the
% Thirteenth Annual International Conference on Research in Computational Molecular 
%Biology (RECOMB 2009)}, May 18-21, 2009 Tucson, AZ, USA

\item
{\bf RNA secondary structure prediction via energy density minimization}.
{\bf {\underline{C Alkan}}}*, E Karako\c{c}*, SC \c{S}ahinalp, P Unrau,
H A Ebhardt, K Zhang, J Buhler.
{\em Proc. of the Tenth Annual International Conference on Research in Computational Molecular Biology
  (RECOMB 2006 - LNBI 3909)}, pp. 130-142,
  April 2-5, 2006 Venice, Italy, 2006.

\end{enumerate}


%\vspace{-.2cm}
% {\bf RNA-RNA interaction prediction and antisense RNA target search}.
%  {\bf {\underline{C Alkan}}}, E Karako\c{c}, J Nadeau, SC \c{S}ahinalp,
%  K Zhang.
%  {\em Proc. of the Ninth Annual International Conference on Research in Computational Molecular Biology
%    (RECOMB 2005 - LNBI 3500)}, pp 152-171, 
%    May 14-18, 2005 Cambridge, MA, USA, 2005.


    
%\vspace{-.2cm}
% {\bf An algorithmic analysis of the role of unequal crossover in
%  alpha-satellite DNA evolution}.
%  {\bf {\underline{C Alkan}}}, JA Bailey, EE Eichler, SC \c{S}ahinalp, E T\"{u}z\"{u}n.
%{\em The 13th International Conference on Genome Informatics}, 
%December 16-18, 2002, Tokyo, Japan, vol.18 pp 93-102, 2002.

\vspace{-.4cm}
\subsection{\small \sc  Unpublished Conference Talks and Posters}
\begin{enumerate}

\item
{\bf Discovery of structural variations in ancient genomes.}
A Soylev, \calkan{}, M Somel. 
Twelfth International Symposium on Health Informatics and Bioinformatics (HIBIT), October 17-18, 2019, İzmir, Turkey.
       {\it Oral presentation by A Soylev.}
       
\item
  {\bf Characterization of large-scale structural variants using Linked-Reads.}
  F Karaoglanoglu, C Ricketts, E Ebren, M Eslami Rasekh, I Hajirasouliha, \calkan{}.
$27^{th}$ Annual
International Conference Intelligent Systems for Molecular Biology (ISMB/ECCB 2019), {\em HiTSeq Track},
 July 23, 2019, Basel, Switzerland. {\it Oral presentation by C Alkan.}

\clearpage
\item
  {\bf SneakySnake: a fast and efficient pre-alignment filter for accelerating approximate string matching.}
  M Alser, \calkan{}, O Mutlu.
$27^{th}$ Annual
International Conference Intelligent Systems for Molecular Biology (ISMB/ECCB 2019), {\em HiTSeq Track},
 July 22-23, 2019, Basel, Switzerland. {\it Poster presentation by M Alser.}

\item
   {\bf BitMAC: an in-memory accelerator for bitvector-based sequence alignment of both
short and long genomic reads.}
  D Senol Cali, C Firtina, JS Kim, Z Bingol, M Alser, \calkan{},
S Ghose, O Mutlu.
$27^{th}$ Annual
International Conference Intelligent Systems for Molecular Biology (ISMB/ECCB 2019), {\em HiTSeq Track},
 July 22-23, 2019, Basel, Switzerland. {\it Poster presentation by C Firtina.}

\item
   {\bf Apollo: a sequencing-technology-independent, scalable, and accurate assembly polishing algorithm.}
  C Firtina, JS Kim, M Alser, D Senol Cali, AE Cicek, \calkan{}, O Mutlu.
$27^{th}$ Annual
International Conference Intelligent Systems for Molecular Biology (ISMB/ECCB 2019), {\em HiTSeq Track},
 July 22-23, 2019, Basel, Switzerland. {\it Poster presentation by C Firtina.}


\item
       {\bf Graph based plasmid identification in bacteria.}
       F Kahveci, Ö. Kalay, A Jain, TF Jesus, JA Carriço, \calkan{}.
       Eleventh International Symposium on Health Informatics and Bioinformatics (HIBIT), October 25-27, 2018, Antalya, Turkey.
       {\it Oral presentation by F Kahveci.}
       
\item
        {\bf Hercules: a profile HMM-based hybrid error correction algorithm for long reads.} C Firtina, Z Bar-Joseph, \calkan{}, AE Cicek. 26$^{th}$ Annual International Conference on Intelligent Systems for Molecular Biology (ISMB 2018), Chicago, IL, United States, July 7-10, 2018.
       {\it Oral presentation by AE Cicek.}

\item
       {\bf Nanopore sequencing technology and tools for genome assembly: computational analysis of the current state, bottlenecks, and future directions.}
       D Senol Cali, JS Kim, S Ghose, \calkan{}, O Mutlu.
       22$^{nd}$ Annual International Conference on Research in Computational Molecular Biology (RECOMB 2018), April 21-24, 2018, Paris, France.
       {\it Poster presentation by D Senol Cali.}

\item
       {\bf Accelerating approximate pattern matching with processing-in-memory (PIM) and single-instruction multiple-data (SIMD) programming.}
       D Senol Cali, Z Bingol, JS Kim, R Ausavarungnirun, S Ghose, \calkan{},
       O Mutlu.
       The Eighth RECOMB Satellite Workshop on Massively Parallel Sequencing, April 19-20, 2018,
       Paris, France.
       {\it Poster presentation by D Senol Cali. Best Poster Award Winner.}

\item
       {\bf Algorithms for structural variation discovery using hybrid sequencing technologies.}
       E Ebren, AB Dinçer, \calkan{}.
       25$^{rd}$ Annual International Conference on Intelligent Systems for Molecular Biology and 16$^{th}$ European Conference on 
       Computational Biology  (ISMB/ECCB 2017), 
       July 21-25, 2017, Prague, Czech Republic.
       {\it Poster presentation by E Ebren.}


\item
       {\bf Discovery of long genomic inversions using long range information.} F Karaoğlanoğlu, M Eslami Rasekh, \calkan{}.
       Tenth International Symposium on Health Informatics and Bioinformatics (HIBIT), June 28-30, 2017, Güzelyurt, Turkish Republic of North Cyprus.
       {\it Oral presentation by F Karaoğlanoğlu.}

\item
       {\bf A profile HMM-based hybrid error correction algorithm for long sequencing reads.} C Fırtına, Z Bar-Joseph, AE Çiçek, \calkan{}.
       Tenth International Symposium on Health Informatics and Bioinformatics (HIBIT), June 28-30, 2017, Güzelyurt, Turkish Republic of North Cyprus.
       {\it Poster presentation by C Fırtına.}

\item
       {\bf LEAP: a generalization of the Landau-Vishkin algorithm with custom gap penalties.} H Xin, JS Kim, S Nahar, C Kingsford, \calkan{}, O Mutlu.
       The Seventh RECOMB Satellite Workshop on Massively Parallel Sequencing, May 7-8, 2017, Hong Kong.
       {\it Oral presentation by H Xin.}

\item
       {\bf Yapısal varyasyonların karakterizasyonu.} A Söylev, \calkan{}. 12$^{th}$ National Medical Genetics Congress, October 7, 2016, Çeşme, Turkey.
       {\it Oral presentation by A Söylev (in Turkish).}
       
\item
{\bf  A new inference attack against kin genomic privacy.}
F Balci, H Kulan, {\bf {\underline{C Alkan}}}$^\ddag$, and E Ayday$^\ddag$. 
{\em Privacy-aware computational genomics (PRIVAGEN 2015)}, 
 September 8, 2015, Tokyo, Japan. {\it Oral and poster presentation by F Balcı.}


 \item
{\bf Identifying anonymous donors of genetic information.}
M Alser, N Almadhoun, A Nouri, {\bf {\underline{C Alkan}}}$^\ddag$, and E Ayday$^\ddag$. 
{\em Privacy-aware computational genomics (PRIVAGEN 2015)}, 
 September 8, 2015, Tokyo, Japan. {\it Poster presentation by M Alser.}


\item
 {\bf BioPeer: A fast and secure peer-to-peer data sharing tool.}
  C Oge, FT Dogan, G Goktepe, F Koc, C Sevim, {\bf {\underline{C Alkan}}}.
{\em The 6$^{th}$ Conference on High Throughput Sequencing Analysis and Algorithms (HiTSeq 2015)}, 
July 10-11, 2015, Dublin, Ireland. {\it Poster presentation by C Öge.}

\item
 {\bf Coinami: A cryptocurrency with DNA sequence alignment as proof-of-work.}
  AM Ileri, HI Ozercan, A Gundogdu, AK Senol, MY Ozkaya, {\bf {\underline{C Alkan}}}.
{\em The 6$^{th}$ Conference on High Throughput Sequencing Analysis and Algorithms (HiTSeq 2015)}, 
July 10-11, 2015, Dublin, Ireland. {\it Oral and poster presentation by C Alkan.}



\item        
       {\bf Optimal Seed Solver: optimizing seed selection in read mapping.}
       H Xin, S Nahar, R Zhu, J Emmons, G Pekhimenko, C Kingsford, \calkan{}$^\ddag$, O Mutlu$^\ddag$.
{\em The 6$^{th}$ Conference on High Throughput Sequencing Analysis and Algorithms (HiTSeq 2015)}, 
July 10-11, 2015, Dublin, Ireland. {\it Poster presentation by H Xin.}



\item
{\bf Discovery of large genomic inversions using pooled clone sequencing.}
ME Rasekh, G Chiatante, M Miroballo, J Tang, M Ventura, CT Amemiya, EE Eichler, F Antonacci$^\ddag$, {\bf {\underline{C Alkan}}}$^\ddag$.
{\em The 6$^{th}$ Conference on High Throughput Sequencing Analysis and Algorithms (HiTSeq 2015)}, 
July 10-11, 2015, Dublin, Ireland. {\it Poster presentation by M Eslami Rasekh.}

\item
  {\bf  A hypergraph-based model for hybrid de novo assembly.}
  S Ashyralyyev, C Firtina, C Aykanat, \calkan{}.
  Bertinoro Computational Biology Meeting, June 17, 2015, Bertinoro, Italy. {\it Oral presentation by S Ashyralyyev.}

\item
 {\bf Massively parallel mapping of next generation sequence reads using GPUs.}
  A Nouri, RO Selvitopi, O Ozturk, O Mutlu$^\ddag$, {\bf {\underline{C Alkan}}}$^\ddag$.
{\em The 20$^{th}$ International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS 2015)}, 
March 14-18, 2015, İstanbul, Turkey. {\it Short talk and poster presented by A Nouri.}

\end{enumerate}


\vspace{-.4cm}
\subsection{\small \sc  Preprints}
 \vspace{-0.6cm}

\small{
Older preprints that are now published in a journal or peer reviewed conference are moved from this section to their relative sections.
}

\begin{enumerate}
 
\item
{\bf Technology dictates algorithms: recent developments in read alignment.}
M Alser, J Rotman, K Taraszka, H Shi, P Icer Baykal, HT Yang, V Xue, S Knyazev, BD Singer, B Balliu, D Koslicki, P Skums, A Zelikovsky, \calkan{}, O Mutlu, S Mangul.
{\it arXiv:2003.00110}, posted Feb 28, 2020.
   
\item
{\bf AirLift: a fast and comprehensive technique for translating alignments between reference genomes.} JS Kim, C Firtina, D Senol Cali, M Alser, N Hajinazar, \calkan{}$^\ddag$, O Mutlu$^\ddag$. {\it arXiv:1912.08735}, posted Dec 18, 2019.

\item
{\bf SneakySnake: a fast and accurate universal genome pre-alignment filter for CPUs, GPUs, and FPGAs.} M Alser, T Shahroodi, J Gomez-Luna, \calkan{}$^\ddag$, O Mutlu$^\ddag$. {\it arXiv:1910.09020}, posted Oct 20, 2019.

\item
{\bf A robust benchmark for germline structural variant detection.} JM Zook, NF Hansen, ND Olson, LM Chapman,  JC Mullikin, C Xiao, S Sherry, S Koren, AM Phillippy,  PC Boutros, SME Sahraeian, V Huang, A Rouette, N Alexander, CE Mason, I Hajirasouliha, C Ricketts, J Lee, R Tearle, IT Fiddes, A Martinez Barrio, J Wala, A Carroll, N Ghaffari, OL Rodriguez, A Bashir,  S Jackman, JJ Farrell, AM Wenger,  \calkan{}, A Soylev, MC Schatz, S Garg, G Church, T Marschall, K Chen, X Fan, AC English, JA Rosenfeld, W Zhou, RE Mills, JM Sage, JR Davis, MD Kaiser, JS Oliver, AP Catalano, MJP Chaisson, N Spies, FJ Sedlazeck, M Salit, the Genome in a Bottle Consortium.
{\it bioRxiv}, doi: 10.1101/664623, posted July 18, 2019.


\item
 {\bf LEAP: a generalization of the Landau-Vishkin algorithm with custom gap penalties.}
 H Xin, J Kim, S Nahar, \calkan{}$^\ddag$, O Mutlu$^\ddag$.
{\it bioRxiv}, doi: 10.1101/133157, posted May 7, 2017.

\item
 {\bf  Coinami: a cryptocurrency with DNA sequence alignment as proof-of-work.}
 AM Ileri, HI Ozercan, A Gundogdu, AK Senol, MYOzkaya, \calkan{}.
{\it arXiv:1602.03031} , posted Feb 9, 2016.

\end{enumerate}

\clearpage
\vspace{-.4cm}

\subsection{\small \sc Software}
\begin{list2}
\item
  Multiple alignment Manipulator (MaM).\\
  {\tt https://github.com/BilkentCompGen/mam}
\item
  taveRNA: RNA suite for RNA folding, RNA-RNA interaction prediction and search.\\
  {\tt http://compbio.cs.sfu.ca/taverna}

\item
  micro-read Fast Alignment Search Tools (mrFAST, mrsFAST, drFAST, and sirFAST).\\
  {\tt https://github.com/BilkentCompGen/mrfast},
  {\tt https://github.com/sfu-compbio/mrsfast},\\
  {\tt https://github.com/BilkentCompGen/drfast},
  {\tt https://github.com/BilkentCompGen/sirfast}
\item
  mrCaNaVaR: characterization of segmental duplications and absolute copy number prediction from read depth.\\
  {\tt https://github.com/BilkentCompGen/mrcanavar}
\item
  VariationHunter/CommonLAW: Structural variation calling algorithm for paired-end, next
  generation sequencing data.\\
  {\tt http://variationhunter.sourceforge.net}
\item
  NovelSeq: computational pipeline fo detect novel sequence insertions using second generation sequencing.\\
  {\tt http://novelseq.sourceforge.net}
\item
  RepeatNet: algorithm to characterize centromeric satellite sequences from paired end sequence data.\\
  {\tt https://github.com/BilkentCompGen/repeatnet}
\item
  SCALCE: Tool to compress FASTQ files. \\
  {\tt https://github.com/sfu-compbio/scalce}
\item
  VALOR: Structural variation discovery using long range information.\\
  {\tt https://github.com/BilkentCompGen/valor}

\item
  Pamir: Novel sequence insertion discovery in multiple samples.\\
  {\tt https://github.com/vpc-ccg/pamir}
\item
  TARDIS: Toolkit for the automated and rapid discovery of structural variants.\\
  {\tt https://github.com/BilkentCompGen/tardis}
\item
  Hercules: Profile HMM-based hybrid error correction algorithm for long reads.\\
  {\tt https://github.com/BilkentCompGen/hercules}
\item
  LaVa: Large structural variation discovery using hybrid sequence data.\\
  {\tt https://github.com/BilkentCompGen/lava}
\item
  SEDEF: Characterization of segmental duplications within genome assemblies.\\
  {\tt https://github.com/vpc-ccg/sedef/}
\item
  GateKeeper: FPGA design for accelerating pre-alignment in DNA short read mapping.\\
  {\tt https://github.com/BilkentCompGen/GateKeeper}
\item
  MAGNET: FPGA-based filtering strategy with high accuracy across different edit distance thresholds.\\
  {\tt https://github.com/BilkentCompGen/MAGNET}
\item
  Shouji: fast and efficient computation of banded sequence alignment.\\
  {\tt https://github.com/CMU-SAFARI/Shouji}
\item
  SneakySnake: approximate alignment computation on CPU, GPU, and FPGA by reducing alignment problem to single net routing problem.\\
  {\tt https://github.com/CMU-SAFARI/SneakySnake}
\item
  BROSV: structural variation breakpoint resolution refiner using split reads.\\
  {\tt https://github.com/BilkentCompGen/brosv}
\end{list2}







