\section{\sc Publications}
                                       
                                       %\vspace*{1cm}
                                       \vspace{-0.5cm}
                                       
                                       \subsection{\small \sc Journal Publications}
                                       \vspace{-0.6cm}
                                       
                                       \small{
                                         Joint first authors are marked with * in case of equal contribution. Joint last authors are marked with $\ddag$.
                                       }


         \vspace{-.2cm}

         {\bf GRIM-Filter: Fast seed location filtering in DNA read mapping using processing-in-memory technologies.}
         J. Kim, D. Senol Cali, H. Xin, D. Lee, S. Ghose, M. Alser, H. Hassan, O. Ergin, \calkan{}$^\ddag$, O. Mutlu$^\ddag$.
         {\em BMC Genomics}, 19 (Suppl 2):89, 2018.\\
         \hspace*{1cm}
          {\footnotesize \em presented at the 16$^{th}$ Asia Pacific Bioinformatics Conference (APBC 2018), January 15-17, 2018, Yokohama, Japan.}

         \vspace{-.2cm}

         {\bf Nanopore sequencing technology and tools for genome assembly: computational analysis of the current state, bottlenecks and future directions.}
         D. Senol Cali, J. Kim, S. Ghose, \calkan{}$^\ddag$, O. Mutlu$^\ddag$.
         {\em Briefings in Bioinformatics}, [epub Apr 2; doi: 10.1093/bib/bby017], 2018.

         \vspace{-.2cm}        

         {\bf Targeting PLK1 overcomes T-DM1 resistance via CDK1-dependent phosphorylation and inactivation of Bcl-2/xL in HER2-positive breast cancer.}
         Ö. Saatci, S. Borgoni, Ö. Akbulut, S. Durmuş, U. Raza, E. Eyüpoğlu, \calkan{}, A. Akyol, Ö. Kütük, S. Wiemann, Ö. Şahin.         
         {\em Oncogene}, Apr; 37(17):2251-2269, 2018.

         \vspace{-.2cm}        

         {\bf Computational pan-genomics: status, promises and challenges.}
         Computational Pan-Genomics Consortium. {\em Briefings in Bioinformatics}, [epub Oct 21, 2016], Jan 1;19(1):118-135, 2018.
         
         \vspace{-.2cm}
         
         {\bf GateKeeper: a new hardware architecture for accelerating pre-alignment in DNA short read mapping.}
         M. Alser, H. Hassan, H. Xin, O. Ergin, O. Mutlu$^\ddag$, \calkan{}$^\ddag$.
         {\em Bioinformatics}, Nov 1; 33(21):3335-63, 2017.


         {\bf Toolkit for automated and rapid discovery of structural variants.}
          A. Soylev, C. Kockan, F. Hormozdiari$^\ddag$, \calkan{}$^\ddag$.
          {\em Methods}, Oct 1, 129:3-7, 2017.
                                       

  \vspace{-.2cm}
                                       

         {\bf Discovery and genotyping of novel sequence insertions in many sequenced individuals.}
         P. Kavak, Y-Y. Lin, I. Numanagić, H. Asghari, T. Güngör, \calkan{}$^\ddag$, F. Hach$^\ddag$.
         {\em Bioinformatics} (ISMB-ECCB 2017 issue), Jul 15; 33 (14): i161-i169, 2017.\\
         \hspace*{1 cm}{\footnotesize \em presented at the 25$^{th}$ Annual International Conference on Intelligent Systems for Molecular Biology and 16$^{th}$ European Conference on 
       Computational Biology  (ISMB/ECCB 2017), 
       July 21-25, 2017, Prague, Czech Republic.}
         
  \vspace{-.2cm}
                                       
         {\bf MAGNET: understanding and improving the accuracy of genome pre-alignment filtering.}
         M. Alser, O. Mutlu$^\ddag$, \calkan{}$^\ddag$. 
         {\em IPSI Transactions on Internet Research}, 13(2), 2017.



         
  \vspace{-.2cm}        
         {\bf Building and improving reference genome assemblies.} K. Meltz-Steinberg, V.A. Schneider, \calkan{}, M.J. Montague, W.C. Warren, D.M. Church, R.K. Wilson.
         {\em Proceedings of the IEEE}, Mar 3, 105(3): 422-435, 2017.



  \vspace{-.2cm}        
         {\bf Discovery of large genomic inversions using long
range information.} M. Eslami Rasekh, G. Chiatante, M. Miroballo, J. Tang, M. Ventura, C.T. Amemiya, E.E. Eichler, F. Antonacci$^\ddag$, \calkan{}$^\ddag$.
         {\em BMC Genomics}, Jan 10;18(1):65, 2017.


  \vspace{-.2cm}        
  {\bf Inter-varietal structural variation in grapevine genomes.}
 M.F. Cardone, P. D'Addabbo, \calkan{}, C. Bergamini, C.R. Catacchio, F. Anaclerio, G. Chiatante, A. Marra, G. Giannuzzi, R. Perniola, M. Ventura, D. Antonacci.
 {\em Plant Journal}, 88(4): 648-661, 2016.

  \vspace{-.2cm}        
  {\bf On genomic repeats and reproducibility.}
  C. Firtina and \calkan{}.
 {\em Bioinformatics}, Aug 1;32(15): 2243-7, 2016.

  \vspace{-.2cm}        
  {\bf Optimal Seed Solver: Optimizing Seed Selection in Read Mapping.}
  H. Xin, S. Nahar, R. Zhu, J. Emmons, G. Pekhimenko, C. Kingsford, \calkan{}$^\ddag$, O. Mutlu$^\ddag$.
 {\em Bioinformatics}, Jun 1;32(11):1632-42, 2016.

  \vspace{-.2cm}        
  {\bf Demographically-based evaluation of genomic regions under selection in domestic dogs.}
A.H. Freedman, R.M. Schweizer, D. Ortega-Del Vecchyo, E. Han, B.W. Davis, I. Gronau, P.M. Silva, M. Galaverni, Z. Fan, P. Marx, B. Lorente-Galdos, O. Ramirez, F. Hormozdiari, \calkan{}, C. Vilà, K. Squire, 
E. Geffen, J. Kusak, A.R. Boyko, H.G. Parker, C. Lee, V. Tadigotla, A. Siepel, C.D. Bustamante, T.T. Harkins, S.F. Nelson, T. Marques-Bonet, E.A. Ostrander, R.K. Wayne, J. Novembre.
 {\em PLoS Genetics}, 12(3):e1005851, 2016.

  \vspace{-.2cm}        
  {\bf Determining the origin of synchronous multifocal bladder cancer by exome sequencing.} 
  Ö. Acar$^*$, E. Özkurt$^*$, G. Demir, H. Saraç, \calkan{}, T. Esen, M. Somel$^\ddag$, Nathan A Lack$^\ddag$.
 {\em BMC Genomics}, Nov 9; 15:871, 2015.

  \vspace{-.2cm}        
  {\bf A global reference for human genetic variation.} The 1000 Genomes Project Consortium.  {\em Nature}, Oct 1; 526 (7571):98-74, 2015.

  \clearpage
  \vspace{-.2cm}        
  {\bf An integrated map of structural variation in 2,504 human genomes.}
  P.H. Sudmant, T. Rausch, E.J. Gardner,  R.E. Handsaker, A. Abyzov, J. Huddleston, Y. Zhang, K. Ye, G. Jun, M.H-Y. Fritz, M.K. Konkel, A. Malhotra, A.M. Stütz, X. Shi, F.P. Casale, J. Chen, 
  F. Hormozdiari, G. Dayama, K. Chen, M. Malig, M.J.P. Chaisson, K. Walter, S. Meiers, S. Kashin, E. Garrison, A. Auton, H.Y.K. Lam, X. J. Mu, \calkan, D. Antaki, T. Bae, E. Cerveira, P. Chines, Z. Chong, 
  L. Clarke, E. Dal, L. Ding, S. Emery, X. Fan, M. Gujral, F. Kahveci, J.M. Kidd, Y. Kong, E-W. Lameijer, S. McCarthy, P. Flicek, R.A.Gibbs, G. Marth, C.E. Mason, A. Menelaou, D.M. Muzny, 
  B.J. Nelson, A. Noor, N.F. Parrish, M. Pendleton, A. Quitadamo, B. Raeder, E.E. Schadt, M. Romanovitch, A. Schlattl, R. Sebra, A.A. Shabalin, A. Untergasser, 
  J.A. Walker, M. Wang, F. Yu, C. Zhang, J. Zhang, X. Zheng-Bradley, W. Zhou, T. Zichner, J. Sebat, M.A. Batzer, S.A. McCarroll, 
  The 1000 Genomes Project Consortium, R.E. Mills, M.B. Gerstein, A. Bashir, O. Stegle, S.E. Devine, C. Lee, E.E. Eichler, J.O. Korbel. 
  {\em Nature}, Oct 1; 526 (7571):75–81, 2015.

  \vspace{-.2cm}        
  {\bf Robustness of massively parallel sequencing platforms.}
  P. Kavak, B. Yüksel, S. Aksu, M.O. Kulekci, T. Güngör, F. Hach, S.C. Sahinalp, Turkish Human Genome Project, {\bf {\underline {C. Alkan}}}$^\ddag$,
  M.S. Sağıroğlu$^\ddag$.    
  {\em PLoS ONE},  Sep 18;10(9):e0138259, 2015.  

  \vspace{-.2cm}        
  {\bf Fast and accurate mapping of Complete Genomics reads.}
  D. Lee, F. Hormozdiari, H. Xin, F. Hach, O. Mutlu$^\ddag$,  {\bf {\underline {C. Alkan}}}$^\ddag$.
  {\em Methods}, Jun;79-80:3-10, 2015. 

  \vspace{-.2cm}        
  {\bf Shifted Hamming Distance: a fast and accurate SIMD-friendly filter to accelerate alignment verification in read mapping.} H. Xin, J. Greth, J. Emmons, 
G. Pekhimenko, C. Kingsford, {\bf {\underline{C. Alkan}}}$^\ddag$,  O. Mutlu$^\ddag$. {\em Bioinformatics},  May 15;31(10):1553-60, 2015.



  \vspace{-.2cm}        
  {\bf Activating mutations of STAT5B and STAT3 in lymphomas derived from $\gamma\delta$-T or NK cells.}
   C. Kucuk, B. Jiang, X. Hu, W. Zhang, J. Chan, W. Xiao, N. Lack,   {\bf {\underline {C. Alkan}}},  J. Williams, K. Avery, P. Kavak, A. Scuto, E. Sen,  P. Gaulard, L. Staudt, J. Iqbal,  W. Zhang,  A. Cornish, Q. Gong, Q.  Yang, H. Sun, F. d'Amore, S. Leppä, W. Liu, K. Fu, L. de Leval, T. McKeithan.
 {\em Nature Communications}, Jan 14;6:6025, 2015.



  \vspace{-.2cm}        
  {\bf Whole genome sequencing of Turkish genomes reveals functional private alleles and impact of genetic interactions with Europe, Asia and Africa.}
  {\bf {\underline {C. Alkan}}}, P. Kavak, M. Somel, O. Gokcumen, S. Uğurlu, E. Dal, K. Buğra-Bilge,  T. Güngör, S.C. Sahinalp, N. Özören, C. Bekpen.
  {\em BMC Genomics}, 15 (1):963, 2014.


  \vspace{-.2cm}        
  {\bf Comparative analysis of the domestic cat genome reveals genetic signatures underlying feline biology and domestication.}
  M.J. Montague, G. Li, B. Gandolfi, R. Khan, B.L. Aken, S.M.J. Searle, P. Minx, L. Hillier, D.C. Koboldt, B.W. Davis, C.A. Driscoll, 
  C.S. Barr, K. Blackistone, J. Quilez, B. Lorente-Galdos, T. Marques-Bonet, {\bf {\underline {C. Alkan}}}, G.W.C. Thomas, M. W. Hahn, M. Menotti-Raymond, 
  S.J. O’Brien, R. Wilson, L.A. Lyons, W.J. Murphy, W.C. Warren. {\em Proc Natl Acad Sci}, Dec 2;111(48):17230-17235, 2014.


  \vspace{-.2cm}        
  {\bf Annotated features of domestic cat – \textit{Felis catus} genome.}
  G. Tamazian, S. Simonov, P. Dobrynin, A. Makunin, A. Logachev, 
  A. Komissarov, A. Shevchenko, V. Brukhin, N. Cherkasov, A. Svitin,
  K-P. Koepfli, J. Pontius, C. A Driscoll, K. Blackistone, C. Barr, 
  D. Goldman, A. Antunes, J. Quilez, B. Lorente-Galdos,  {\bf {\underline {C. Alkan}}},
  T. Marques-Bonet, M. Menotti-Raymond, V.A. David, K. Narfström, S.J. O’Brien.
  {\em GigaScience}, Aug 5; 3:(13), 2014.
                                       
  \vspace{-.2cm}        
  {\bf mrsFAST-Ultra: a compact, SNP-aware mapper for high performance sequencing applications.}
    F. Hach$^*$,
    I. Sarrafi$^*$,
    F. Hormozdiari,
    {\bf {\underline {C. Alkan}}},
    E.E. Eichler,   S.C. Sahinalp.
    {\em Nucl Acids Research}, Jul;42(Web Server issue):W494-500, 2014.

  \vspace{-.2cm}        
         {\bf Early postzygotic mutations contribute to de novo variation in a healthy monozygotic twin pair.}
         G.M. Dal, B. Ergüner, M.S. Sağıroğlu, B. Yüksel, O.E. Onat, {\bf {\underline {C. Alkan}}}, T. Özçelik. 
         {\em J Med Genet}, 51(7):455-459, 2014.


  \vspace{-.2cm}        
         {\bf Genome sequencing highlights the dynamic early history of dogs.} 
         A.H. Freedman, I. Gronau, R.M. Schweizer, D. Ortega-Del Vecchyo, E. Han, P.M. Silva, 
         M. Galaverni, Z. Fan, P. Marx, B. Lorente-Galdos, H. Beale, O. Ramirez, F. Hormozdiari, 
         {\bf {\underline {C. Alkan}}}, 
         C. Vilà, K. Squire, E. Geffen, J. Kusak, A.R. Boyko, H.G. Parker, 
         C. Lee, V. Tadigotla, A. Siepel, C.D. Bustamante, T.T. Harkins, S.F. Nelson, 
         E.A. Ostrander, T. Marques-Bonet, R.K. Wayne, J. Novembre. 
         {\em PLoS Genetics}, 10(1): e1004016, 2014.


 \vspace{-.2cm}        
        {\bf Reconstructing complex regions of genomes using long-read sequencing technology.}
         J. Huddleston, S. Ranade, M. Malig, F. Antonacci, M. Chaisson, L. Hon, P.H. Sudmant, T.A. Graves, 
         {\bf {\underline{C. Alkan}}}, M.Y. Dennis, R.K. Wilson, S.W. Turner, J. Korlach, E.E. Eichler. 
         {\em Genome Research},  24(4):688-96, 2014.


 \vspace{-.2cm}        
        {\bf Rates and patterns of great ape retrotransposition.}
        F. Hormozdiari, M.K. Konkel, J. Prado-Martinez, G. Chiatante, I. Hernando-Herraez, J.A. Walker, B. Nelson, {\bf {\underline {C. Alkan}}}, P.H. Sudmant, J. Huddleston, C.R. Catacchio, A. Ko, 
        M. Malig, C. Baker, T. Marques-Bonet, M. Ventura, M.A. Batzer, and E.E. Eichler. 
        {\em Proc Natl Acad Sci}, Aug 13;110(33):13457-62, 2013.
                             

 \vspace{-.2cm}
        {\bf Great ape genetic diversity and population history.}
        J. Prado-Martinez, P.H. Sudmant, J.M. Kidd, H. Li, J.L. Kelley, B. Lorente-Galdos, K.R. Veeramah, A.E. Woerner, T.D. O’Connor, G. Santpere, A. Cagan, C. Theunert, F. Casals, H. Laayouni, K. Munch, A. Hobolth, A.E. Halager, M. Malig, J. Hernandez-Rodriguez, I. Hernando-Herraez, K. Prüfer, M. Pybus, L. Johnstone, M. Lachmann, {\bf {\underline {C. Alkan}}}, D. Twigg, N. Petit, C. Baker, F. Hormozdiari, M. Fernandez-Callejo, M. Dabad, M.L. Wilson, L. Stevison, C. Camprubí, T. Carvalho, A. Ruiz-Herrera, L. Vives, M. Mele, T. Abello, I. Kondova, R.E. Bontrop, A. Pusey, F. Lankester, J.A. Kiyang, R.A. Bergl, E. Lonsdorf, S. Myers, M. Ventura, P. Gagneux, D. Comas, H. Siegismund, J. Blanc, L. Agueda-Calpena, M. Gut, L. Fulton, S.A. Tishkoff, J.C. Mullikin, R.K. Wilson, I.G. Gut, M. Katherine Gonder, O.A. Ryder, B.H. Hahn, A. Navarro, J.M. Akey, J. Bertranpetit, D. Reich, T. Mailund, M.H. Schierup, C. Hvilsom, A.M. Andrés, J.D. Wall, C.D. Bustamante, M.F. Hammer, E.E. Eichler, T. Marques-Bonet. 
        {\em Nature}, 499(7459):471-475, 2013.

        

\vspace{-.2cm}
        {\bf The genome sequencing of an albino Western lowland gorilla reveals inbreeding in the wild.}
        J. Prado-Martinez, I. Hernando-Herraez, B. Lorente-Galdos, M. Dabad, O. Ramirez, C. Baeza-Delgado, C. Morcillo-Suarez, 
        {\bf {\underline {C. Alkan}}}, F. Hormozdiari, E. Raineri, J. Estellé, M. Fernandez-Callejo, M. Valles, L. Ritscher, T. Schöneberg, E. de la Calle-Mustienes, 
        S. Casillas, R. Rubio-Acero, M. Melé, J. Engelken, M. Caceres, J.L. Gomez-Skarmeta, M. Gut, J. Bertranpetit, I.G. Gut, T. Abello, 
        E.E. Eichler, I. Mingarro, C. Lalueza-Fox, A. Navarro, T. Marques-Bonet.
        {\em BMC Genomics}, May 31;14(1):363, 2013.

        
 \vspace{-.2cm}
        {\bf Refinement and discovery of new hotspots of copy-number variation associated with autism spectrum disorder.}
        S. Girirajan*, M.Y. Dennis*, C. Baker, M. Malig, B.P. Coe, C.D. Campbell, K. Mark, T.H. Vu,
        {\bf {\underline {C. Alkan}}}, Z. Cheng, L.G. Biesecker, R. Bernier, E.E. Eichler.
        {\em Am J Hum Genet.}, Feb 7;92(2):221-37, 2013.

 \vspace{-.2cm}
        {\bf Accelerating read mapping with FastHASH.}
        H. Xin, D. Lee, F. Hormozdiari, S. Yedkar, O. Mutlu$^\ddag$, {\bf {\underline {C. Alkan}}}$^\ddag$.
        {\em BMC Genomics}, 14(Suppl 1):S13, 2013.\\
        \hspace*{1cm} {\footnotesize {\em presented at the  11$^{th}$  Asia Pacific Bioinformatics Conference,
            Jan. 21-23, 2013, Vancouver, BC, Canada}}
        
 \vspace{-.2cm}
        {\bf An integrated map of genetic variation from 1,092 human genomes.}
        The 1000 Genomes Project Consortium. 
        {\em Nature}, Nov 1;491(7422):56-65, 2012.
        
 \vspace{-.2cm}
        {\bf SCALCE: boosting sequence compression algorithms using locally consistent encoding.}
        F. Hach, I. Numanagi\`{c}, {\bf {\underline {C. Alkan}}}, S. Cenk Sahinalp.  
        {\em Bioinformatics}, Dec 1;28(23):3051-57, 2012.

 \vspace{-.2cm}
        {\bf A high-coverage genome sequence from an archaic Denisovan individual.}
        M. Meyer, M. Kircher, M-T. Gansauge, H. Li, F. Racimo, S. Mallick, J.G. Schraiber, F. Jay, K. Pr\"{u}fer, C. de Filippo, P.H. Sudmant, 
        {\bf {\underline {C. Alkan}}}, Q. Fu, R. Do, N. Rohland, A. Tandon, M. Siebauer, R.E. Green, 
        K. Bryc, A.W. Briggs, U. Stenzel, J. Dabney, J. Shendure, J. Kitzman, M.F. Hammer, M.V. Shunkov, 
        A.P. Derevianko, N. Patterson, A.M. Andr\'{e}s, E.E. Eichler, M. Slatkin, D. Reich, J. Kelso, S. P\"{a}\"{a}bo. 
        {\em Science}, 338(6014):222-226, 2012.

 \vspace{-.2cm}
        {\bf The bonobo genome compared with the chimpanzee and human genomes.}
        The International Gorilla Genome Sequencing and Analysis Consortium.
        {\em Nature}, 486(7404):527-531, 2012.


\vspace{-.2cm}
{\bf Insights into hominid evolution from the gorilla genome sequence.}
The International Gorilla Genome Sequencing and Analysis Consortium.
{\em Nature}, 483(7388): 169-175, 2012. 

\vspace{-.2cm}
{\bf Copy number variation of individual cattle genomes using next-generation sequencing.} 
D.M. Bickhart. Y. Hou, S.G. Schroeder, {\bf {\underline {C. Alkan}}}, M.F. Cardone, L.K. Matukumalli, J. Song, 
R.D. Schnabel, M. Ventura, J.F. Taylor, J.F. Garcia, C.P. Van Tassell, T.S. Sonstegard, E.E. Eichler, G.E. Liu. 
{\em Genome Research}, Apr;22(4):778-90, 2012.

\vspace{-.2cm}
{\bf Detection of structural variants and indels within exome data.} E. Karakoc, {\bf {\underline {C. Alkan}}}, B.J. O'Roak, 
M.Y. Dennis, L. Vives, K. Mark, M.J. Rieder, D.A. Nickerson, E.E. Eichler. {\em Nature Methods}, 9(2): 176-178, 2012.


\vspace{-.2cm}
{\bf Identification and validation of a novel mature microRNA encoded by the Merkel cell polyomavirus in human Merkel cell carcinomas.}
S. Lee, K.G. Paulson, E.P. Murchison, O.K. Afanasiev, {\bf {\underline {C. Alkan}}}, J.H. Leonard, D.R. Byrd, G.J. Hannon, 
P. Nghiem. {\em J Clin Virol.} Nov; 52(3):272-275, 2011. 

        \clearpage

\vspace{-.2cm}
{\bf A hexanucleotide repeat expansion in C9ORF72 is the cause of chromosome 9p21-linked ALS-FTD.}  
A.E. Renton, E. Majounie, A. Waite, J. Simón-Sánchez, S. Rollinson, J.R. Gibbs, J.C. Schymick, H. Laaksovirta, J.C. van Swieten, L. Myllykangas, 
H. Kalimo, A. Paetau, Y. Abramzon, A.M. Remes, A. Kaganovich, S.W. Scholz, J. Duckworth, J. Ding, D.W. Harmer, D.G. Hernandez, J.O. Johnson, 
K. Mok, M. Ryten, D. Trabzuni, R.J. Guerreiro, R.W. Orrell, J. Neal, A. Murray, J. Pearson, I.E. Jansen, D. Sondervan, H. Seelaar, D. Blake, 
K. Young, N. Halliwell, J.B. Callister, G. Toulson, A. Richardson, A. Gerhard, J. Snowden, D. Mann, D. Neary, M.A. Nalls, T. Peuralinna, 
L. Jansson, V.M. Isoviita, A.L. Kaivorinne, M. Hölttä-Vuori, E. Ikonen, R. Sulkava, M. Benatar, J. Wuu, A. Chiò, G. Restagno, 
G. Borghero, M. Sabatelli, The ITALSGEN Consortium, D. Heckerman, E. Rogaeva, L. Zinman, J.D. Rothstein, M. Sendtner, C. Drepper, E.E. Eichler, 
{\bf {\underline {C. Alkan}}}, Z. Abdullaev, S.D. Pack, A. Dutra, E. Pak, J. Hardy, A. Singleton, N.M. Williams, P. Heutink, S. Pickering-Brown, 
H.R. Morris, P.J. Tienari, B.J. Traynor. {\em Neuron}, Oct 20; 72(2):257-268, 2011.

\vspace{-.2cm}
{\bf Gorilla genome structural variation reveals evolutionary parallelisms with chimpanzee.}
M. Ventura, C.R. Catacchio, {\bf {\underline {C. Alkan}}}, T. Marques-Bonet, S. Sajjadian, T.A. Graves, F. Hormozdiari, A. Navarro, 
M. Malig, C. Baker, C. Lee, E.H. Turner, L. Chen, J.M. Kidd, N. Archidiacono, J. Shendure, R.K. Wilson, E.E. Eichler.
{\em Genome Research}, Oct;21(10):1640-9, 2011.


\vspace{-.2cm}
{\bf Sensitive and fast mapping of di-base encoded reads.}
F. Hormozdiari*, F. Hach*, S.C. Sahinalp, E.E. Eichler, {\bf {\underline {C. Alkan}}}.
{\em Bioinformatics}, Jul 15;27(14):1915-21, 2011.



\vspace{-.2cm}
{\bf \textit {Alu} repeat discovery and characterization within human genomes}.
F. Hormozdiari*, {\bf {\underline {C. Alkan*}}}, M. Ventura*, I. Hajirasouliha, M. Malig, 
F. Hach, D. Yorukoglu, P. Dao, M. Bakshi, S.C. Sahinalp, E.E. Eichler.
{\em Genome Research}, Jun;21(6):840-9, 2011.

\vspace{-.2cm}
{\bf Genome structural variation discovery and genotyping}. 
{\bf {\underline {C. Alkan}}}, B.P. Coe, E.E. Eichler.
{\em Nature Reviews Genetics}, 12:363-376, 2011.


\vspace{-.2cm}
{\bf {\em Clcn4-2} genomic structure differs between the X locus in Mus spretus and the autosomal 
locus in Mus musculus: AT motif enrichment on the X}.  
D.K. Nguyen, F. Yang, R. Kaul, {\bf {\underline {C. Alkan}}}, A. Antonellis, K.F. Friery, 
B. Zhu, P.J. de Jong, C.M. Disteche. 
{\em Genome Research}, 21(3):402-409, 2011.


\vspace{-.2cm}
{\bf Mapping copy number variation at fine scale by population scale genome sequencing}.
R.E. Mills*, K. Walter*, C. Stewart*, R.E. Handsaker*, K. Chen*, 
{\bf {\underline {C. Alkan}*}}, A. Abyzov*, S.C. Yoon*, K. Ye*, R.K. Cheetham, 
A. Chinwalla, D.F. Conrad, Y. Fu, F. Grubert, I. Hajirasouliha, 
F. Hormozdiari, L.M. Iakoucheva, Z. Iqbal, S. Kang, J.M. Kidd, 
M.K. Konkel, J. Korn, E. Khurana, D. Kural, H.Y.K. Lam, J. Leng, 
R. Li, Y. Li, C-Y. Lin, R. Luo, X.J. Mu, J. Nemesh,
H.E. Peckham, T. Rausch, A. Scally, X. Shi, M.P. Stromberg, 
A.M. St\"{u}tz, A. E. Urban, J.A. Walker, J. Wu, Y. Zhang, 
Z.D. Zhang, M.A. Batzer, L. Ding, G.T. Marth, G. McVean, 
J. Sebat, M. Snyder, J. Wang, K. Ye, E.E. Eichler, 
M.B. Gerstein, M.E. Hurles, C. Lee, S.A. McCarroll,  J.O. Korbel.
{\em Nature}, 470(7332):56-65, 2011.


\vspace{-.2cm}
{\bf Comparative and demographic analysis of orangutan genomes}. 
International Orangutan Genome Sequencing and Analysis Consortium.
{\em Nature}, 469(7331):529-533, 2011.

\vspace{-.2cm}
{\bf Haplotype resolved genome sequencing of a Gujarati Indian individual}.
J.O. Kitzman, A.P. MacKenzie, A. Adey, J.B. Hiatt, R.P. Patwardhan, 
P.H. Sudmant, S.B. Ng, {\bf {\underline{C. Alkan}}}, R. Qiu, E.E.
Eichler, J. Shendure.
{\em Nature Biotechnology}, 29(1):59-63, 2011.


\vspace{-.2cm}
{\bf Limitations of next-generation genome assembly}.
{\bf {\underline {C. Alkan}}}, S. Sajjadian, E.E. Eichler.
{\em Nature Methods}, 8(1):61-65, 2011. \\
\hspace*{1 cm}{\footnotesize {\it Highlighted in ``Assemblies: the good, the bad, the ugly'', E. Birney, 
Nature Methods, 8(1):59-60, 2011.}}



\vspace{-.2cm}
{\bf Genome-wide characterization of centromeric satellites from multiple mammalian genomes}.
{\bf {\underline {C. Alkan*}}}, M.F. Cardone*, C.R. Catacchio, F. Antonacci,
 S.J. O'Brien, O.A. Ryder, S. Purgato, M. Zoli, G. Della Valle, E.E. Eichler, M. Ventura.
{\em Genome Research}, 21(1): 137-145, 2011.


\vspace{-.2cm}
{\bf Genetic history of an archaic hominin group from Denisova Cave in Siberia}.
D. Reich, R.E. Green, M. Kircher, J. Krause, 
N. Patterson, E.Y. Durand, B. Viola, A.W. Briggs, 
U. Stenzel, P.L.F. Johnson, T. Maricic, J.M. Good, 
T. Marques-Bonet, {\bf {\underline {C. Alkan}}}, Q. Fu, S. Mallick, H. Li, 
M. Meyer, E.E. Eichler, M. Stoneking, M. Richards, 
S. Talamo, M.V. Shunkov, A.P. Derevianko, J-J. Hublin, 
J. Kelso, M. Slatkin, S. P\"{a}\"{a}bo.
{\em Nature}, Dec; 468(7327):1053-1060, 2010.

\vspace{-.2cm}
{\bf Diversity of human copy number variation and multicopy genes}. P.H. Sudmant, J.O. Kitzman, F. Antonacci, 
{\bf {\underline {C. Alkan}}}, M. Malig, A. Tsalenko, N. Sampas, L. Bruhn, J. Shendure, The 1000 Genomes Project Consortium, E.E. Eichler.
{\em Science}, Oct; 330(6004):641-646, 2010.

\vspace{-.2cm}
{\bf A map of human genome variation from population scale sequencing}. The 1000 Genomes Project Consortium.
{\em Nature}, Oct; 467(7319):1061-1073, 2010.

\vspace{-.2cm}
{\bf A large and complex structural polymorphism at 16p12.1 underlies microdeletion disease risk}. F. Antonacci, J.M. Kidd,
 T. Marques-Bonet, B. Teague, M. Ventura, S. Girirajan, {\bf {\underline {C. Alkan}}}, C.D. Campbell, L. Vives, M. Malig, 
J.A. Rosenfeld, B.C. Ballif, L.G. Shaffer, T.A. Graves, R.K. Wilson, D.C. Schwartz, E.E. Eichler. {\em Nature 
Genetics}, Sep; 42(9):745-750, 2010.

\vspace{-.2cm}
{\bf mrsFAST: a cache-oblivious algorithm for short-read mapping}. F.  Hach,  F. Hormozdiari, {\bf {\underline {C. Alkan}}}, F. Hormozdiari,
 I. Birol,  E.E. Eichler, S.C. Sahinalp. {\em Nature Methods}, Aug;7(8):576-7, 2010.

\vspace{-.2cm}
 {\bf A draft sequence of the Neandertal genome}. R.E. Green, J. Krause, 
A.W. Briggs, T. Maricic, U. Stenzel, M. Kircher, N. Patterson, 
H. Li, W. Zhai, M.H-Y. Fritz, N.F. Hansen, E.Y. Durand, 
A-S. Malaspinas, J.D. Jensen, T. Marques-Bonet, {\bf {\underline {C. Alkan}}}, K. Pr\"{u}fer, M. Meyer, H.A. Burbano, J.M. Good, R. Schultz, A. Aximu-Petri, 
A. Butthof, B. H\"{o}ber, B. H\"{o}ffner, M. Siegemund, A. Weihmann, C.
Nusbaum, E.S. Lander, C. Russ, N. Novod, J. Affourtit, M. Egholm, 
C. Verna, P. Rudan, D. Brajkovic, Z. Kucan, I. Gusic, V.B. 
Doronichev, L.V. Golovanova, C. Lalueza-Fox, M. de la Rasilla, J. Fortea, 
A. Rosas, R.W. Schmitz, P.L.F. Johnson, E.E. Eichler, D. Falush, E. 
Birney, J.C. Mullikin, M. Slatkin, R. Nielsen, J. Kelso, M. Lachmann, 
D. Reich, S. P\"{a}\"{a}bo. {\em Science}, 7 May, 328 (5979):710-722, 2010. \\
\hspace*{1 cm}{\footnotesize {\it Recipient of the 2010 AAAS Newcomb Cleveland Prize.}}


\vspace{-.2cm}
{\bf Characterization of missing human genome sequences and
copy-number polymorphic insertions}.
J.M. Kidd, N. Sampas, F. Antonacci, T. Graves, R. Fulton, H.S. Hayden, {\bf {\underline{C. Alkan}}},
 M. Malig, M. Ventura, G. Giannuzzi, J. Kallicki, P. Anderson, A. Tsalenko, 
N.A. Yamada, P. Tsang, R. Kaul, R.K. Wilson, L. Bruhn, E.E. Eichler.
{\em Nature Methods}, May, 7 (5):365-371, 2010.


\vspace{-.2cm}
{\bf Next-generation VariationHunter: combinatorial algorithms for transposon insertion discovery}.
F. Hormozdiari, I. Hajirasouliha, P. Dao, F. Hach, D. Yorukoglu, {\bf {\underline{C. Alkan}}},
 E.E. Eichler, S.C. Sahinalp.
{\em Bioinformatics}, Jun 15; 26(12):i350-i357, 2010. \\
\hspace*{1cm} {\footnotesize {\em presented at the 18$^{th}$ Annual International Conference on Intelligent Systems
for Molecular Biology (ISMB 2010), July 11-13, 2010, Boston, MA, USA}}



\vspace{-.2cm}
{\bf Detection and characterization of novel sequence insertions using paired-end next-generation sequencing}.
 I. Hajirasouliha*, F. Hormozdiari*, {\bf {\underline{C. Alkan}}}*, J.M. Kidd, I. Birol, E.E. Eichler,
 S.C. Sahinalp.
{\em Bioinformatics}, May 15;26(10):1277-83, 2010. \\
\hspace*{1cm} {\footnotesize {\em presented at theConference on High Throughput Sequencing Analysis and Algorithms (HiTSeq 2010), 
    Special Interest Group of ISMB 2010: July 9-10 2010, Boston, MA, USA}}


\vspace{-.2cm}
{\bf Complete Khoisan and Bantu genomes from southern Africa}.
 S.C. Schuster, W. Miller, A. Ratan, L.P. Tomsho, B. Giardine, L.R. Kasson, R.S.
 Harris, D.C. Petersen, F. Zhao, J. Qi, {\bf \underline{C. Alkan}}, J.M. Kidd, Y. Sun, D.I. Drautz, 
P. Bouffard, D.M. Muzny, J.G. Reid, L.V. Nazareth, Q. Wang, R. Burhans, C. Riemer, 
N.E. Wittekindt, P. Moorjani, E.A. Tindall, C.G. Danko, W.S. Teo, A.M. Buboltz, 
Z. Zhang, Q. Ma, A. Oosthuysen, A.W. Steenkamp, H. Oostuisen, P. Venter, J. 
Gajewski, Y. Zhang, B.F. Pugh, K.D. Makova, A. Nekrutenko, E.R. Mardis, N. Patterson, 
T.H. Pringle, F. Chiaromonte, J.C. Mullikin, E.E. Eichler, R.C. Hardison, R.A. Gibbs, T.T. 
Harkins, V.M. Hayes. 
{\em Nature}, Feb, 463(7283):943-947, 2010.


\vspace{-.2cm}
{\bf Personalized copy-number and segmental duplication maps using next-generation sequencing}.
{\bf {\underline{C. Alkan}}}, J.M. Kidd, T. Marques-Bonet, G. Aksay, F. Antonacci, F. Hormozdiari, J. O. Kitzman, 
C. Baker, M. Malig, O. Mutlu, S.C. Sahinalp, R. A. Gibbs, E.E. Eichler.  
{\em Nature Genetics},  Oct, 41(10):1061-1067, 2009.\\
\hspace*{1 cm}{\footnotesize {\it Highlighted in "Mapping duplicated sequences", DY Chiang and SA McCarroll, Nature Biotechnology, Nov; 27(11):1001-2, 2009.}}


\vspace{-.2cm}
{\bf Sequence and structural variation in a human genome uncovered by short-read, massively parallel ligation sequencing using two base encoding}.
K.J. McKernan, H.E. Peckham, G.L. Costa, S.F. McLaughlin, Y. Fu, E.F. Tsung, C.R. Clouser, C. Duncan, J.K. Ichikawa, C.C. Lee, Z. Zhang, 
S.S. Ranade, E.T. Dimalanta,  F.C. Hyland, T.D. Sokolsky, L. Zhang, J.A. Sheridan, H. Fu, C.L. Hendrickson, B. Li, L. Kotler, J.R. Stuart, 
J.A. Malek, J.M. Manning, A.A. Antipova, D.S. Perez, M.P. Moore, K.C. Hayashibara, M.R. Lyons, R.E. Beaudoin, B.E. Coleman, M.W. Laptewicz, 
A.E. Sannicandro, M.D. Rhodes, R.K. Gottimukkala, S. Yang, V. Bafna, A. Bashir, A. MacBride, {\bf \underline{C. Alkan}}, J.M. Kidd, E.E. Eichler, 
M.G. Reese, F.M. De La Vega, A.P. Blanchard. 
{\em Genome Research}, Sep, 19(9): 1527-1541, 2009.


\vspace{-.2cm}
{\bf  New insights into centromere organization and evolution from the white-cheeked gibbon and marmoset}.
A. Cellamare,    C.R. Catacchio,  {\bf \underline{C. Alkan}}, G. Giannuzzi, F. Antonacci, M.F. Cardone, G. Della Valle, M. Malig, M. Rocchi, E.E. Eichler, M. Ventura.
{\em Mol Biol Evol}, Aug; 26(8):1889-1900, 2009.

\vspace{-.2cm}
{\bf MoDIL: detecting small indels from clone-end sequencing with mixtures of distributions}.
S. Lee, F. Hormozdiari, {\bf {\underline{C. Alkan}}}, M. Brudno.
{\em Nature Methods},  Jul, 6(7):473-4, 2009.


\clearpage

\vspace{-.2cm}
{\bf  Combinatorial algorithms for structural variation detection in high throughput sequenced genomes}.
F. Hormozdiari*, {\bf {\underline{C. Alkan}}}*, E.E. Eichler, S.C. \c{S}ahinalp. 
{\em Genome Research}, Jul, 19(7):1270-8, 2009.\\
\hspace*{1cm} {\footnotesize {\it presented at the
 Thirteenth Annual International Conference on Research in Computational Molecular 
Biology (RECOMB 2009), May 18-21, 2009 Tucson, AZ, USA}}



\vspace{-.2cm}

{\bf Comparative analysis of Alu repeats in primate genomes}.  G.E. Liu, {\bf {\underline{C. Alkan}}}, L. Jiang, S. Zhao, E.E. Eichler. 
{\em Genome Research}, 19(5):876-885, 2009.




\vspace{-.2cm}
{\bf Death and resurrection of the human {\em IRGM} gene}. C. Bekpen, T. Marques-Bonet,
{\bf {\underline{C. Alkan}}}, F. Antonacci, M. B. Leogrande, M. Ventura, J.M. Kidd, P. Siswara, J. C. Howard, E.E. Eichler. {\em PLoS Genetics}, March 2009; 5(3):e1000403, 2009.

\vspace{-.2cm}

{\bf A burst of segmental duplications in the genome of the African great ape ancestor}. T. Marques-Bonet, J.M. Kidd, M. Ventura, T.A. Graves, Z. Cheng, L.W. Hillier, Z. Jiang, 
C. Baker, R. Malfavon-Borja, L.A. Fulton, {\bf {\underline{C. Alkan}}}, G. Aksay, S. Girirajan,
 P. Siswara, L. Chen, M.F. Cardone, A. Navarro, E.R. Mardis,
 R.K. Wilson, E.E. Eichler. {\em Nature}, Feb 12 2009; 457(7231):877-881, 2009.


\vspace{-.2cm}
 {\bf Mapping and sequencing of structural variation from eight human genomes}.
 J.M. Kidd, G.M. Cooper, W.F. Donahue, H.S. Hayden, 
 N. Sampas, T. Graves, N. Hansen, B. Teague, {\bf {\underline{C. Alkan}}},  F. Antonacci, 
 E. Haugen, T. Zerr, N.A. Yamada, P. Tsang,  T.L. Newman, E. T\"{u}z\"{u}n, 
 Z. Cheng, H.M. Ebling, N. Tusneem, R. David, W. Gillett, K.A. Phelps, 
 D. Saranga, A. Brand, W. Tao, E. Gustafson, K. McKernan, L. Chen, 
 M. Malig, J.D. Smith, S.A. McCarroll, D.A. Altshuler,  
 D.A. Peiffer, M. Dorschner, J. Stamatoyannopoulos, D. Schwartz,  
 D.A. Nickerson, J.C. Mullikin, R.K. Wilson, L. Bruhn, 
 M.V. Olson, R. Kaul, D.R. Smith, E.E. Eichler.
 {\em Nature}, May 1, 2008; 453(7191):56-64, 2008.


\vspace{-.2cm}
 {\bf Optimal design of oligonucleotide microarrays for measurement of DNA copy number}.
 A.J. Sharp, A. Itsara, Z. Cheng, {\bf {\underline{C. Alkan}}}, S. Schwartz, E.E. Eichler.
 {\em Human Molecular Genetics}, Nov 15; 16(22):2770-2779, 2007.


%\clearpage

\vspace{-.2cm}
 {\bf Organization and evolution of primate centromeric DNA from whole genome shotgun sequence data}.
 {\bf {\underline{C. Alkan}}}, M. Ventura, N. Archidiacono, M. Rocchi, S.C. \c{S}ahinalp, E.E. Eichler.
 {\em PLoS Computational Biology}, 3(9): e181, September 2007.


\vspace{-.2cm}
 {\bf taveRNA: a web suite for RNA algorithms and applications}.
  C. Aksay, R. Salari, E. Karako\c{c}, {\bf {\underline{C. Alkan}}}, S.C. \c{S}ahinalp.
  {\em Nucleic Acids Research}, July 1, 2007; Vol. 35 (Web Server Issue): W325-329, 2007.

\vspace{-.2cm}
 {\bf RNA-RNA interaction prediction and antisense RNA target search}.
  {\bf {\underline{C. Alkan}}}, E. Karako\c{c}, J. Nadeau, S.C. \c{S}ahinalp,
  K. Zhang.
  {\em Journal of Computational Biology}, March 2006; Vol 13, No 2: 267-282, 2006. \\
\hspace*{1cm} {\footnotesize {\it presented at the Ninth Annual International Conference on Research in Computational Molecular Biology
    (RECOMB 2005 - LNBI 3500), pp 152-171, 
    May 14-18, 2005 Cambridge, MA, USA, 2005.}}


\vspace{-.2cm}
{\bf Manipulating multiple sequence alignments via MaM and  WebMaM}.
{\bf {\underline{C. Alkan}}}, E. T\"{u}z\"{u}n, J. Buard, F. Lethiec,
E.E. Eichler, J.A. Bailey, S.C. \c{S}ahinalp.
{\em Nucleic Acids Research}, July 1, 2005; Vol. 33 (Web Server issue):
W295-W298, 2005.

\vspace{-.2cm}
 {\bf The role of unequal crossover in alpha-satellite 
   DNA evolution: a computational analysis}.
  {\bf {\underline{C. Alkan}}}, E.E. Eichler, J.A. Bailey, S.C. \c{S}ahinalp, E. T\"{u}z\"{u}n.
  {\em Journal of Computational Biology}, Vol. 11, No.5: 933-944, 2004. \\
\hspace*{1cm}  {\footnotesize {\it presented at the 13$^{th}$ International Conference on Genome Informatics, 
December 16-18, 2002, Tokyo, Japan, vol.18 pp 93-102, 2002.}}

\vspace{-.2cm}
  {\bf The structure and evolution of centromeric transition regions within
    the human genome}.
  X. She, J.E. Horvath, Z. Jiang, G. Liu, T. S. Furey,
  L. Christ, R. Clark, T. Graves, C.L. Gulden, {\bf \underline{C. Alkan}}, J.A. Bailey, S.C. \c{S}ahinalp, 
  M. Rocchi, D. Haussler, R.K. Wilson, W. Miller, S. Schwartz, E.E. Eichler.
  {\em Nature}, Aug 19, 2004; 430(7002):857-64, 2004.


\vspace{-.2cm}
  {\bf Analysis of primate genomic variation reveals a repeat-driven 
    expansion of the human genome}.
  G. Liu, NISC Comparative Sequencing Program, S. Zhao, J.A. Bailey, 
  S.C. \c{S}ahinalp, {\bf \underline{C. Alkan}}, E. T\"{u}z\"{u}n, E.D. Green, E.E. Eichler.
  {\em Genome Research}, 13(3):358-368, 2003.

\vspace{-.2cm}
  {\bf Divergent origins and concerted expansion of two segmental
    duplications on 
    chromosome 16}.
  E.E. Eichler, M.E. Johnson, {\bf \underline{C. Alkan}}, E. T\"{u}z\"{u}n, C. \c{S}ahinalp,
    D. Misceo, 
    N. Archidiacono, and M. Rocchi.
    {\em Journal of Heredity}, 92: 462-468, 2001.


\vspace{-.4cm}
\subsection{\small \sc  Peer-Reviewed Conference Publications}
\vspace{-.4cm}
       {\small
         %Note: In CS disciplines papers in highly ranked conferences are fully refereed 
%and are regarded as highly as the top journal papers. 
%In computational molecular biology RECOMB and ISMB are generally accepted as the 
%top conferences, with 10-15\% acceptance rates.
Note that selected papers accepted to some conferences such as ISMB and RECOMB are published
in special issues of journals. Such publications are listed under Journal Publications with a note to the conference above.
Joint first authors are marked with * in case of equal contribution.
Joint last authors are marked with $\ddag$.
}


%  \vspace{-.2cm}        
%         {\bf Genome Read In-Memory (GRIM) Filter: fast seed location filtering in DNA read mapping using processing-in-memory technologies.}
%         J. Kim, D. S. Cali, H. Xin, D. Lee, S. Ghose, M. Alser, H. Hassan, O. Ergin, \calkan{}$^\ddag$, O. Mutlu$^\ddag$.
%         The 16$^{th}$ Asia Pacific Bioinformatics Conference (APBC 2018), January 15-17, 2018, Yokohama, Japan.


% \clearpage
%  \vspace{-.2cm}        
%         {\bf Discovery and genotyping of novel sequence insertions in many sequenced individuals.}
%         Pınar Kavak, Yen-Yi Lin, Ibrahim Numanagić, Hossein Asghari, Tunga Güngör, \calkan{}$^\ddag$, Faraz Hach$^\ddag$.
%       25$^{th}$ Annual International Conference on Intelligent Systems for Molecular Biology and 16$^{th}$ European Conference on 
%       Computational Biology  (ISMB/ECCB 2017), 
%       July 21-25, 2017, Prague, Czech Republic.



\vspace{-.2cm}
{\bf Can you really anonymize the donors of genomic data in today's digital world?}
M. Alser, N. Almadhoun, A. Nouri, {\bf {\underline{C. Alkan}}}$^\ddag$, and E. Ayday$^\ddag$. 
{\em 10$^{th}$ International Workshop on Data Privacy Management (DPM 2015)}, 
 September 21-22, 2015, Vienna, Austria.


\vspace{-.2cm}

{\bf Improving genome assemblies using multi-platform sequence data.}
P. Kavak, B. Ergüner, D. Üstek, B. Yüksel, M.Ş. Sağıroğlu, T. Güngör and \calkan{}.
{\em 12$^{th}$ Computational Intelligence methods for Bioinformatics and Biostatistics (CIBB 2015)}, 
 September 10-12, 2015, Naples, Italy.


%\vspace{-.2cm}
%{\bf Accelerating read mapping with FastHASH.}
%H. Xin, D. Lee, F. Hormozdiari, S. Yedkar, O. Mutlu$^\ddag$, {\bf {\underline {C. Alkan}}}$^\ddag$.
%{\em  Proc. of the 11$^{th}$  Asia Pacific Bioinformatics Conference},
%Jan. 21-23, 2013, Vancouver, BC, Canada

%\vspace{-.2cm}
%{\bf Detection and characterization of novel sequence insertions using paired-end next-generation sequencing},
% I. Hajirasouliha*, F. Hormozdiari*, {\bf {\underline{C. Alkan}}}*, J.M. Kidd, I. Birol, E.E. Eichler,
% S.C. Sahinalp.
%{\em  Proc. of the 11$^{th}$  Conference on High Throughput Sequencing Analysis and Algorithms, Special Interest
%Group of ISMB 2010 (HiTSeq 2010): July 9-10 2010, Boston, MA, USA}

%\vspace{-.2cm}
%{\bf Next-generation VariationHunter: combinatorial algorithms for transposon insertion discovery}.
%F. Hormozdiari, I. Hajirasouliha, P. Dao, F. Hach, D. Yorukoglu, {\bf {\underline{C. Alkan}}},
% E.E. Eichler, S.C. Sahinalp.
%{\em Proc. of the 18$^{th}$ Annual International Conference on Intelligent Systems
%for Molecular Biology (ISMB 2010)}, July 11-13, 2010, Boston, MA, USA


%\clearpage

%\vspace{-.2cm}
%{\bf  Combinatorial algorithms for structural variation detection in high throughput sequenced genomes}.
%F. Hormozdiari*, {\bf {\underline{C. Alkan}}}*, E.E. Eichler, S.C. \c{S}ahinalp.
%{\em Proc. of the
% Thirteenth Annual International Conference on Research in Computational Molecular 
%Biology (RECOMB 2009)}, May 18-21, 2009 Tucson, AZ, USA

\vspace{-.2cm}
{\bf RNA secondary structure prediction via energy density minimization}.
{\bf {\underline{C. Alkan}}}*, E. Karako\c{c}*, S.C. \c{S}ahinalp, P. Unrau,
H. A. Ebhardt, K. Zhang, J. Buhler.
{\em Proc. of the Tenth Annual International Conference on Research in Computational Molecular Biology
  (RECOMB 2006 - LNBI 3909)}, pp. 130-142,
  April 2-5, 2006 Venice, Italy, 2006.


%\vspace{-.2cm}
% {\bf RNA-RNA interaction prediction and antisense RNA target search}.
%  {\bf {\underline{C. Alkan}}}, E. Karako\c{c}, J. Nadeau, S.C. \c{S}ahinalp,
%  K. Zhang.
%  {\em Proc. of the Ninth Annual International Conference on Research in Computational Molecular Biology
%    (RECOMB 2005 - LNBI 3500)}, pp 152-171, 
%    May 14-18, 2005 Cambridge, MA, USA, 2005.


    
%\vspace{-.2cm}
% {\bf An algorithmic analysis of the role of unequal crossover in
%  alpha-satellite DNA evolution}.
%  {\bf {\underline{C. Alkan}}}, J.A. Bailey, E.E. Eichler, S.C. \c{S}ahinalp, E. T\"{u}z\"{u}n.
%{\em The 13th International Conference on Genome Informatics}, 
%December 16-18, 2002, Tokyo, Japan, vol.18 pp 93-102, 2002.

\vspace{-.4cm}
\subsection{\small \sc  Unpublished Conference Talks and Posters}

\vspace{-.2cm}
       {\bf Nanopore Sequencing Technology and Tools for Genome Assembly: Computational Analysis of the Current State, Bottlenecks, and Future Directions.}
       Damla Senol Cali, Jeremie S. Kim, Saugata Ghose, Can Alkan, Onur Mutlu.
       22$^{nd}$ Annual International Conference on Research in Computational Molecular Biology (RECOMB 2018), April 21-24, 2018, Paris, France.
       {\it Poster presentation by D. Senol Cali.}

\vspace{-.2cm}
       {\bf Accelerating Approximate Pattern Matching with Processing-In-Memory (PIM) and Single-Instruction Multiple-Data (SIMD) Programming.}
       Damla Senol Cali, Zulal Bingol, Jeremie Kim, Rachata Ausavarungnirun, Saugata Ghose, Can Alkan,
       Onur Mutlu.
       The Eighth RECOMB Satellite Workshop on Massively Parallel Sequencing, April 19-20, 2018,
       Paris, France.
       {\it Poster presentation by D. Senol Cali. Best Poster Award Winner.}


\vspace{-.2cm}
       {\bf Algorithms for structural variation discovery using hybrid sequencing technologies.}
       Ezgi Ebren, Ayşe Berceste Dinçer, Can Alkan.
       25$^{rd}$ Annual International Conference on Intelligent Systems for Molecular Biology and 16$^{th}$ European Conference on 
       Computational Biology  (ISMB/ECCB 2017), 
       July 21-25, 2017, Prague, Czech Republic.
       {\it Poster presentation by E. Ebren.}

\vspace{-.2cm}
       {\bf Discovery of long genomic inversions using long range information.} Fatih Karaoğlanoğlu, Marzieh Eslami Rasekh, Can Alkan.
       Tenth International Symposium on Health Informatics and Bioinformatics (HIBIT), June 28-30, 2017, Güzelyurt, Turkish Republic of North Cyprus.
       {\it Oral presentation by F. Karaoğlanoğlu.}

\vspace{-.2cm}
       {\bf A Profile HMM-based hybrid error correction algorithm for long sequencing reads.} Can Fırtına, Ziv Bar-Joseph, Ercüment Çiçek, Can Alkan.
       Tenth International Symposium on Health Informatics and Bioinformatics (HIBIT), June 28-30, 2017, Güzelyurt, Turkish Republic of North Cyprus.
       {\it Poster presentation by C. Fırtına.}

\vspace{-.2cm}
       {\bf LEAP: a generalization of the Landau-Vishkin algorithm with custom gap penalties.} Hongyi Xin, Jeremie Kim, Sunny Nahar, Carl Kingsford, Can Alkan, Onur Mutlu.
       The Seventh RECOMB Satellite Workshop on Massively Parallel Sequencing, May 7-8, 2017, Hong Kong.
       {\it Oral presentation by H. Xin.}

\vspace{-.2cm}
       {\bf Yapısal varyasyonların karakterizasyonu.} Arda Söylev, \calkan{}. 12$^{th}$ National Medical Genetics Congress, October 7, 2016, Çeşme, Turkey.
       {\it Oral presentation by A. Söylev (in Turkish).}
       
\vspace{-.2cm}
{\bf  A new inference attack against kin genomic privacy.}
F. Balci, H. Kulan, {\bf {\underline{C. Alkan}}}$^\ddag$, and E. Ayday$^\ddag$. 
{\em Privacy-aware computational genomics (PRIVAGEN 2015)}, 
 September 8, 2015, Tokyo, Japan. {\it Oral and poster presentation by Fatma Balcı.}

\vspace{-.2cm}
{\bf Identifying anonymous donors of genetic information.}
M. Alser, N. Almadhoun, A. Nouri, {\bf {\underline{C. Alkan}}}$^\ddag$, and E. Ayday$^\ddag$. 
{\em Privacy-aware computational genomics (PRIVAGEN 2015)}, 
 September 8, 2015, Tokyo, Japan. {\it Poster presentation by Mohammed Alser.}

\vspace{-.2cm}
 {\bf BioPeer: A fast and secure peer-to-peer data sharing tool.}
  C. Oge, F.T. Dogan, G. Goktepe, F. Koc, C. Sevim, {\bf {\underline{C. Alkan}}}.
{\em The 6$^{th}$ Conference on High Throughput Sequencing Analysis and Algorithms (HiTSeq 2015)}, 
July 10-11, 2015, Dublin, Ireland. {\it Poster presentation by Cihad Öge.}

 \clearpage
\vspace{-.2cm}
 {\bf Coinami: A cryptocurrency with DNA sequence alignment as proof-of-work.}
  A.M. Ileri, H.I. Ozercan, A. Gundogdu, A.K. Senol, M.Y. Ozkaya, {\bf {\underline{C. Alkan}}}.
{\em The 6$^{th}$ Conference on High Throughput Sequencing Analysis and Algorithms (HiTSeq 2015)}, 
July 10-11, 2015, Dublin, Ireland. {\it Oral and poster presentation by H. İbrahim Özercan.}



\vspace{-.2cm}        
       {\bf Optimal Seed Solver: optimizing seed selection in read mapping.}
       H. Xin, S. Nahar, R. Zhu, J. Emmons, G. Pekhimenko, C. Kingsford, \calkan{}$^\ddag$, O. Mutlu$^\ddag$.
{\em The 6$^{th}$ Conference on High Throughput Sequencing Analysis and Algorithms (HiTSeq 2015)}, 
July 10-11, 2015, Dublin, Ireland. {\it Poster presentation by Hongyi Xin.}

\vspace{-.2cm}
{\bf Discovery of large genomic inversions using pooled clone sequencing.}
M.E. Rasekh, G. Chiatante, M. Miroballo, J. Tang, M. Ventura, C.T. Amemiya, E.E. Eichler, F. Antonacci$^\ddag$, {\bf {\underline{C. Alkan}}}$^\ddag$.
{\em The 6$^{th}$ Conference on High Throughput Sequencing Analysis and Algorithms (HiTSeq 2015)}, 
July 10-11, 2015, Dublin, Ireland. {\it Poster presentation by Marzieh Eslami Rasekh.}


\vspace{-.2cm}
  {\bf  A hypergraph-based model for hybrid de novo assembly.}
  S. Ashyralyyev, C. Firtina, C. Aykanat, \calkan{}.
  Bertinoro Computational Biology Meeting, June 17, 2015, Bertinoro, Italy. {\it Oral presentation by Shatlyk Ashyralyyev}

\vspace{-.2cm}}
 {\bf Massively parallel mapping of next generation sequence reads using GPUs.}
  A. Nouri, R.O. Selvitopi, O. Ozturk, O. Mutlu$^\ddag$, {\bf {\underline{C. Alkan}}}$^\ddag$.
{\em The 20$^{th}$ International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS 2015)}, 
March 14-18, 2015, İstanbul, Turkey. {\it Short talk and poster presented by Azita Nouri.}



\vspace{-.4cm}
\subsection{\small \sc  Preprints}

\vspace{-.2cm}
 {\bf Hercules: a profile HMM-based hybrid error correction algorithm for long reads.}
 C. Firtina, Z. Bar-Joseph, \calkan{}$^\ddag$, E. Cicek$^\ddag$.
{\it bioRxiv}, doi: 10.1101/233080, posted Dec 13, 2017.

\vspace{-.2cm}
 {\bf LEAP: a generalization of the Landau-Vishkin algorithm with custom gap penalties.}
 H. Xin, J. Kim, S. Nahar, \calkan{}$^\ddag$, O. Mutlu$^\ddag$.
{\it bioRxiv}, doi: 10.1101/133157, posted May 7, 2017.

\vspace{-.2cm}
 {\bf  Coinami: a cryptocurrency with DNA sequence alignment as proof-of-work.}
 A.M. Ileri, H.I. Ozercan, A. Gundogdu, A.K. Senol, M.Y.Ozkaya, \calkan{}.
{\it arXiv:1602.03031} , posted Feb 9, 2016.



\vspace{-.4cm}

\subsection{\small \sc Software}
\begin{list2}
\item
  Multiple alignment Manipulator (MaM).\\
  {\tt https://github.com/BilkentCompGen/mam}
\item
  taveRNA: RNA suite for RNA folding, RNA-RNA interaction prediction and search.\\
  {\tt http://compbio.cs.sfu.ca/taverna}

\item
  micro-read Fast Alignment Search Tools (mrFAST, mrsFAST, drFAST, and sirFAST).\\
  {\tt https://github.com/BilkentCompGen/mrfast},
  {\tt https://github.com/sfu-compbio/mrsfast},\\
  {\tt https://github.com/BilkentCompGen/drfast},
  {\tt https://github.com/BilkentCompGen/sirfast}
\item
  mrCaNaVaR: characterization of segmental duplications and absolute copy number prediction from read depth.\\
  {\tt https://github.com/BilkentCompGen/mrcanavar}
\item
  VariationHunter/CommonLAW: Structural variation calling algorithm for paired-end, next
  generation sequencing data.\\
  {\tt http://variationhunter.sourceforge.net}
\item
  NovelSeq: computational pipeline fo detect novel sequence insertions using second generation sequencing.\\
  {\tt http://novelseq.sourceforge.net}
\item
  RepeatNet: algorithm to characterize centromeric satellite sequences from paired end sequence data.\\
  {\tt https://github.com/BilkentCompGen/repeatnet}
\item
  SCALCE: Tool to compress FASTQ files. \\
  {\tt https://github.com/sfu-compbio/scalce}
\item
  VALOR: Structural variation discovery using long range information.\\
  {\tt https://github.com/BilkentCompGen/valor}
\item
  Pamir: Novel sequence insertion discovery in multiple samples.\\
  {\tt https://github.com/vpc-ccg/pamir}
\item
  TARDIS: Toolkit for the automated and rapid discovery of structural variants.\\
  {\tt https://github.com/BilkentCompGen/tardis}
\item
  Hercules: Profile HMM-based hybrid error correction algorithm for long reads.\\
  {\tt https://github.com/BilkentCompGen/hercules}
\item
  LaVa: Large structural variation discovery using hybrid sequence data.\\
  {\tt https://github.com/BilkentCompGen/lava}
\end{list2}







